### 2021-07-16 paper/main.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{paralist}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\newcommand{\tool}{\textsc{SALVO}\xspace}
\newboolean{showcomments}
\setboolean{showcomments}{true}         
%\setboolean{showcomments}{false} 
\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[2]{
  \fbox{\bfseries\sffamily\scriptsize#1}
     {\sf\small$\blacktriangleright$\textit{\textcolor{red}{#2}}$\blacktriangleleft$}
   }
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\cvsversion}{}
  }

\newcommand\alessio[1]{\nb{Alessio}{#1}} 
\newcommand\vuong[1]{\nb{Vuong}{#1}} 
\newcommand\stefan[1]{\nb{Stefan}{#1}}

\title{\tool: Automated Generation of Diversified Tests from Existing Maps
\alessio{Title is not final}
}

\author{\IEEEauthorblockN{Alessio Gambi}
\IEEEauthorblockA{\textit{Passau University} \\
Passau, Germany \\
alessio.gambi@uni-passau.de}
\and
\IEEEauthorblockN{Vuong Nguyen}
\IEEEauthorblockA{\textit{Passau University} \\
Passau, Germany \\
nguyen58@ads.uni-passau.de}
\and
\IEEEauthorblockN{Stefan Huber}
\IEEEauthorblockA{\textit{Passau University} \\
Passau, Germany \\
stefan.huber.niedling@outlook.com}
}

\maketitle

% Another thing: as the deadline for the final phase of the challenge is fast approaching, we would like to encourage you to submit a paper describing the results of your (team)work.
% The papers are accepted as part of the 2021 IEEE AI Testing Conference and should be submitted via EasyChair (make sure that you select the "Only for IEEE AV AI Test Challenge 2021" option). The submissions are expected to be 6-10 pages long and should present an overview of the scenarios created during phases 1 and 2 of the challenge as well as results of test execution accompanied by the conclusion. The format of the papers is described on the main conference CFP page.  
% The deadline for paper submissions is July 23. We will be sending notifications of acceptance during the week of August 9.

\begin{abstract}
Testing self-driving car software using photo-realistic and physically accurate simulators is becoming a widely adopted practice. Simulators enable the automated execution of many tests that possibly implement safety-critical driving scenarios that are unlikely or simply too dangerous to put into practice. However, despite the speed-up achieved by simulation-based testing, fundamental challenges are yet to be addressed before achieving cost-effective testing of self-driving cars.

In this paper, we present \tool, an approach to automated self-driving car software testing that addresses the following challenges:
\begin{inparaenum}[(i)]
\item systematically identifying relevant driving scenarios among the myriad of potential driving scenarios that can be defined over existing maps;
\item selecting driving scenarios that minimize testing effort while ensuring quantifiably different behaviors, 
and \item 
automatically generating test cases that implement those relevant and diversified driving scenarios.
\end{inparaenum}

We demonstrated \tool in the context of the 2021 IEEE Test AI Challenge
by testing state-of-art self-driving car software using an industrial driving simulator. In a matter of minutes, \tool identified many relevant tests from five maps of different sizes and complexity (up to $170$ junctions) and selected $20\%$ of those test cases for execution in the best case. 
%
The evaluation results showed that tests cases generated by \tool resulted in quantifiably different trajectories of the test subject and exposed issues in the test subject and its integration with the simulation platform.
\alessio{Update numbers with missing maps}
\end{abstract}

% CubeTown
%1. 10 paths
%2. distance 1.9: 8 paths
%3. 10 cells: 5 paths
%4. 12 intersections
%BorregasAve
%1. 28 paths
%2. distance 1.9: 20 paths
%3. 10 cells: 16 paths
%4. 29 intersections
%Shalun
%1. 140 paths
%2. distance 1.9: 110 paths
%3. 10 cells: 33 paths
%4. 169 intersections

\begin{IEEEkeywords}
\alessio{todo}
\end{IEEEkeywords}

\section{Introduction}
\alessio{todo}

%\section*{Acknowledgment}
%
%The preferred spelling of the word ``acknowledgment'' in America is without 
%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
%acknowledgments in the unnumbered footnote on the first page.

% References
\bibliographystyle{IEEEtran}
\bibliography{biblio}

\end{document}

### 2021-07-16 deliverable2/runner.py
Use Choice options in cli command to select maps

@@ -13,19 +13,28 @@ LEFT = -1.9
 MIDDLE = 0
 RIGHT = 1.9
 
+MAPS = {
+    "BorregasAve": "maps/BorregasAve.xodr",
+    "CubeTown": "maps/CubeTown.xodr",
+    "AutonomouStuff": "maps/AutonomouStuff.xodr",
+    "SanFrancisco": "maps/SanFrancisco.xodr",
+    "Shalun": "maps/Shalun.xodr",
+    "Gomentum": "maps/Gomentum.xodr"
+}
+
 
 @cli.command()
-@click.option('--map_file', help="Name of map file")
+@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
 @click.option('--before_junction', type=int, help="Distance before entering junction")
 @click.option('--after_junction', type=int, help="Distance after leaving junction")
 @click.option('--filter', nargs=3, is_flag=False, flag_value="Flag", type=(str, float, bool),
               help="[Optional] Filter Arguments: Method (Distance or Feature), Measure (Min-distance or the number "
                    "of cells) and Display Plot or not")
 def generate_all_paths(map_file, before_junction, after_junction, filter):
-    map_list = map_file.split('/')
+    map_list = MAPS[map_file].split('/')
     mmap = {
         "name": map_list[len(map_list) - 1].split('.')[0],
-        "path": map_file
+        "path": MAPS[map_file]
     }
     expm = Experiment(mmap=mmap, name="Generate All Possible Paths", plan=StraightModel)
     if filter is not None:
@@ -38,7 +47,7 @@ def generate_all_paths(map_file, before_junction, after_junction, filter):
 
 
 @cli.command()
-@click.option('--map_file', help="Name of map file")
+@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
 @click.option('--before_junction', type=int, help="Distance before entering junction")
 @click.option('--after_junction', type=int, help="Distance after leaving junction")
 @click.option('--samples', type=int, help="How many tests to sample for Test Pools")
@@ -46,10 +55,10 @@ def generate_all_paths(map_file, before_junction, after_junction, filter):
               help="[Optional] Filter Arguments: Method (Distance or Feature), Measure (Min-distance or the number "
                    "of cells) and Display Plot or not")
[…]

### 2021-07-16 paper/main.tex
Included new data from maps

@@
 by testing state-of-art self-driving car software using an industrial driving simulator.
-In a matter of minutes, \tool identified many relevant tests from five maps of different sizes and complexity (up to $170$ junctions) and selected $20\%$ of those test cases for execution in the best case.
+In a matter of minutes, \tool analyzed five maps of different complexity (from $2$ to more than $15$ junctions),
+identified more than $1100$ relevant driving scenarios in them, and selected on average half of
+them for the execution.
 %
-The evaluation results showed that tests cases generated by \tool resulted in quantifiably different trajectories of the test subject and exposed issues in the test subject and its integration with the simulation platform.
-\alessio{Update numbers with missing maps}
+The evaluation results showed that tests cases generated by \tool from the selected driving scenarios
+resulted in quantifiably different trajectories of the test subject and exposed issues in it.
+
 \end{abstract}
 
-% CubeTown
+%CubeTown
 %1. 10 paths
@@
 %3. 10 cells: 5 paths
-%4. 12 intersections
+%4. 2 intersections
 %BorregasAve
@@
 %3. 10 cells: 16 paths
-%4. 29 intersections
+%4. 2 intersections
 %Shalun
@@
 %3. 10 cells: 33 paths
-%4. 169 intersections
+%4. 14 intersections
+%SanFrancisco
+%1. 806 paths
+%2. distance 1.9: 535 paths
+%3. 10 cells: 52 paths
+%4. 89 intersections
+%Gomentum
+%1. 126 paths
+%2. distance 1.9: 110 paths
+%3. 10 cells: 25 paths
+%4. 25 intersections
 

### 2021-07-16 deliverable2/models/experiment.py
Remove un-necessary files

@@ -35,6 +35,7 @@ class Experiment:
                 scenario = Scenario(start=scenario_data["start"],
                                     end=scenario_data["end"],
                                     mmap=self.mmap["name"],
+                                    dvmap=self.mmap["dv"],
                                     tc_id=id)
                 self.plan.run(scenario)
             else:
@@ -42,6 +43,7 @@ class Experiment:
                                     end=scenario_data["end"],
                                     mmap=self.mmap["name"],
                                     tc_id=id,
+                                    dvmap=self.mmap["dv"],
                                     park=scenario_data["park"])
                 p = ParkingModel()
                 p.set_distance(distance)

### 2021-07-16 deliverable2/salvo.py

@@ -1,4 +1,4 @@
-from models import Experiment, Filter, MapModel
+from models import Experiment
 from models.plan import StraightModel, ParkingModel
 import click
 import random
@@ -13,19 +13,39 @@ LEFT = -1.9
 MIDDLE = 0
 RIGHT = 1.9
 
+MAPS = {
+    "BorregasAve": "maps/BorregasAve.xodr",
+    "CubeTown": "maps/CubeTown.xodr",
+    "AutonomouStuff": "maps/AutonomouStuff.xodr",
+    "SanFrancisco": "maps/SanFrancisco.xodr",
+    "Shalun": "maps/Shalun.xodr",
+    "Gomentum": "maps/Gomentum.xodr"
+}
+
+DV_MAPS = {
+    "BorregasAve": "Borregas Ave",
+    "CubeTown": "Cubetown",
+    "AutonomouStuff": "Autonomous Stuff",
+    "SanFrancisco": "San Francisco",
+    "Shalun": "Shalun",
+    "Gomentum": "Gomentum"
+}
+
+
 
 @cli.command()
-@click.option('--map_file', help="Name of map file")
+@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
 @click.option('--before_junction', type=int, help="Distance before entering junction")
 @click.option('--after_junction', type=int, help="Distance after leaving junction")
 @click.option('--filter', nargs=3, is_flag=False, flag_value="Flag", type=(str, float, bool),
               help="[Optional] Filter Arguments: Method (Distance or Feature), Measure (Min-distance or the number "
                    "of cells) and Display Plot or not")
 def generate_all_paths(map_file, before_junction, after_junction, filter):
-    map_list = map_file.split('/')
+    map_list = MAPS[map_file].split('/')
     mmap = {
         "name": map_list[len(map_list) - 1].split('.')[0],
-        "path": map_file
+        "path": MAPS[map_file],
+        "dv": DV_MAPS[map_file]
     }
     expm = Experiment(mmap=mmap, name="Generate All Possible Paths", plan=StraightModel)
     if filter is not None:
@@ -38,7 +58,7 @@ def generate_all_paths(map_file, before_junction, after_junction, filter):
 
 
 @cli.command()
-@click.option('--map_file', help="Name of map file")
[…]

### 2021-07-21 deliverable2/salvo.py
Update README file

@@ -34,9 +34,9 @@ DV_MAPS = {
 
 
 @cli.command()
-@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
-@click.option('--before_junction', type=int, help="Distance before entering junction")
-@click.option('--after_junction', type=int, help="Distance after leaving junction")
+@click.option('--map-file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
+@click.option('--before-junction', type=int, help="Distance before entering junction")
+@click.option('--after-junction', type=int, help="Distance after leaving junction")
 @click.option('--filter', nargs=3, is_flag=False, flag_value="Flag", type=(str, float, bool),
               help="[Optional] Filter Arguments: Method (Distance or Feature), Measure (Min-distance or the number "
                    "of cells) and Display Plot or not")
@@ -58,9 +58,9 @@ def generate_all_paths(map_file, before_junction, after_junction, filter):
 
 
 @cli.command()
-@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
-@click.option('--before_junction', type=int, help="Distance before entering junction")
-@click.option('--after_junction', type=int, help="Distance after leaving junction")
+@click.option('--map-file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
+@click.option('--before-junction', type=int, help="Distance before entering junction")
+@click.option('--after-junction', type=int, help="Distance after leaving junction")
 @click.option('--samples', type=int, help="How many tests to sample for Test Pools")
 @click.option('--filter', nargs=3, is_flag=False, flag_value="Flag", type=(str, float, bool),
               help="[Optional] Filter Arguments: Method (Distance or Feature), Measure (Min-distance or the number "
@@ -91,10 +91,10 @@ def run_scenarios(map_file, before_junction, after_junction, samples, filter):
 
 
 @cli.command()
-@click.option('--map_file', type=click.Choice(['SanFrancisco', 'Gomentum', 'CubeTown', 'BorregasAve', 'Shalun'], case_sensitive=True))
-@click.option('--before_junction', type=int, help="Distance before entering junction")
[…]

### 2021-07-21 deliverable2/models/lanelet/lanelet.py
Revised the entire README file. There are few todos to address

@@ -143,7 +143,7 @@ class LaneLet:
                         # else:
                             # print(l1, "FAKE OVERLAP WITH", l2, "AREA", overlapping_area_p1, "--", overlapping_area_p2)
                     except Exception as e:
-                        print(">> Discard problemaic lanelet", e)
+                        print(">> Discard problematic lanelet", e)
 
 
         # Initialize and then merge all the groups of lanelets that have shared items

### 2021-08-20 paper/main.tex
Updated title
Pre CR-Version

--- 2021-07-16 paper/main.tex
@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage[utf8]{inputenc}
+
 \usepackage{cite}
@@
 \usepackage{paralist}
+\usepackage{float}
+\usepackage{booktabs}
+\usepackage{hyperref}
 
@@
 
-\title{\tool: Automated Generation of Diversified Tests from Existing Maps
-\alessio{Title is not final}
-}
+%\title{\tool: Automated Generation of Diversified Tests for Self-driving Cars based on Photo-Realistic Maps}
+\title{\tool: Automated Generation of Diversified Tests for Self-driving Cars from Existing Maps}
 
-\author{\IEEEauthorblockN{Alessio Gambi}
-\IEEEauthorblockA{\textit{Passau University} \\
-Passau, Germany \\
-alessio.gambi@uni-passau.de}
-\and
+\author{
 \IEEEauthorblockN{Vuong Nguyen}
-\IEEEauthorblockA{\textit{Passau University} \\
+\IEEEauthorblockA{\textit{University of Passau} \\
 Passau, Germany \\
@@
 \IEEEauthorblockN{Stefan Huber}
-\IEEEauthorblockA{\textit{Passau University} \\
+\IEEEauthorblockA{\textit{University of Passau} \\
 Passau, Germany \\
 stefan.huber.niedling@outlook.com}
+\and
+\IEEEauthorblockN{Alessio Gambi}
+\IEEEauthorblockA{\textit{University of Passau} \\
+Passau, Germany \\
+alessio.gambi@uni-passau.de}
 }
@@
 
-% Another thing: as the deadline for the final phase of the challenge is fast approaching, we would like to encourage you to submit a paper describing the results of your (team)work.
-% The papers are accepted as part of the 2021 IEEE AI Testing Conference and should be submitted via EasyChair (make sure that you select the "Only for IEEE AV AI Test Challenge 2021" option).
-The submissions are expected to be 6-10 pages long and should present an overview of the scenarios created during phases 1 and 2 of the challenge as well as results of test execution accompanied by the conclusion.
-The format of the papers is described on the main conference CFP page.
-% The deadline for paper submissions is July 23. We will be sending notifications of acceptance during the week of August 9.
+\begin{abstract}
+% Testing self-driving car software using photo-realistic and accurate physical simulators is becoming a widely adopted practice.
+Simulators enable the automated execution of many tests that possibly implement safety-critical driving scenarios that are too dangerous to put into practice.
+However, despite the speed-up achieved by using simulators, fundamental challenges are yet to be addressed before achieving cost-effective testing of self-driving cars.
+% %
+% In this paper, we present \tool, an approach to automated self-driving car software testing that addresses some of those challenges. Specifically, \tool
+% \begin{inparaenum}[(i)]
+% \item systematically identifies relevant driving scenarios among a myriad of potential driving scenarios that can be defined over existing maps;
+% \item selects driving scenarios that reduce testing efforts while ensuring quantifiable different behaviors, and 
+% \item automatically generates test cases that implement those diversified driving scenarios.
+% \end{inparaenum}
+% %
+% We demonstrated \tool in the 2021 IEEE Test AI Challenge
+% by testing state-of-the-art self-driving car software using an industrial driving simulator.
+% In a matter of minutes, \tool analyzed five maps of different complexity levels (from $2$ to more than $15$ intersections), identified more than $1100$ relevant driving scenarios, and selected on average half of them for the execution.
+% %
+% The evaluation results showed that tests cases generated by \tool from the selected driving scenarios resulted in quantifiable different trajectories followed by the test subject and exposed issues in it.
 
-\begin{abstract}
-Testing self-driving car software using photo-realistic and physically accurate simulators is becoming a widely adopted practice.
-Simulators enable the automated execution of many tests that possibly implement safety-critical driving scenarios that are unlikely or simply too dangerous to put into practice.
-However, despite the speed-up achieved by simulation-based testing, fundamental challenges are yet to be addressed before achieving cost-effective testing of self-driving cars.
+%For testing self-driving cars simulations are heavily utilized since these allow running many simulations at once and allow enforcing critical situations without endangering any other drivers or pedestrians.
+%For increasing the quality of tests photo-realistic maps and accurate physical simulators are a widely adopted and still growing practice.
+%However, despite these advantages there are still fundamental challenges including cost-effectiveness and further increasing the degree of automation for finding or generating critical tests.\\
+%This paper presents \tool, an approach
+%(1) to systematically identify relevant driving scenarios among the myriad of potential driving scenarios,
+%(2) to select scenarios that reduce the required overall testing efforts by ensuring quantifiability and diversity of the expected behaviours of self-driving cars for succeeding scenarios and
+%(3) to generate those test cases.\\
+%We demonstrated \tool at the 2021 IEEE Test AI Challenge by running state-of-the-art self-driving car software in an industrial driving simulator against our generated test cases.
+%In a matter of minutes, \tool analyzed five maps of different complexity (from 2 to more than 15 intersections), identified more than 1100 relevant driving scenarios and selected on average half of them for actual test executions.
+%The evaluation results showed that the generated test cases resulted in quantifiable and diverse trajectories and exposed issues of the self-driving car software.
 
-In this paper, we present \tool, an approach to automated self-driving car software testing that addresses the following challenges:
-\begin{inparaenum}[(i)]
-\item systematically identifying relevant driving scenarios among the myriad of potential driving scenarios that can be defined over existing maps;
-\item selecting driving scenarios that minimize testing effort while ensuring quantifiably different behaviors, 
-and \item 
-automatically generating test cases that implement those relevant and diversified driving scenarios.
+Simulation-based tests are more cost-effective and less dangerous than field tests; hence, they are becoming the norm for thoroughly testing self-driving cars in virtual environments.
+High-quality simulation-based testing requires physically accurate computer simulations,  detailed and photo-realistic maps, and systematic approaches for generating tests.
+Moreover, since creating detailed maps is a manual process, they are expensive, and testers should avoid wasting such valuable resources, for example, by generating irrelevant test cases.
+To address those issues, we propose \tool a fully automated approach to identify quantifiably diverse and critical driving scenarios that can be instantiated on existing high-definition maps and implement them in an industrial driving simulator as executable test cases.
+The evaluation of \tool in the context of the 2021 IEEE Test AI Challenge showed that it could analyze maps of different complexity and identify many critical driving scenarios in minutes.
+Furthermore, the tests \tool generated stressed a state-of-art self-driving car software in quantifiably diverse ways and exposed issues with its implementation.
+\end{abstract}
+
+ \begin{IEEEkeywords}
+Test Case Generation, Autonomous Vehicles, Software-in-the-loop, Diversity, Feature Space
+ \end{IEEEkeywords}
+
+\section{Introduction and Motivation}
+Self-driving cars promise to reduce traffic accidents \cite{peden2016status}, increase fuel efficiency \cite{zamzuri2016current} and enhance comfort %and safety for elders and disabled people 
+ \cite{harper2016estimating}.
+Testing self-driving car software is laborious and challenging since their development is still in an early stage and testing them lacks of standardized procedures and established approaches \cite{gambi2019generating}.\par
+
+Nevertheless, many researchers and organisations put a lot of effort in exploring and devising testing approaches to increase the quality of autonomous vehicles before they roam the thoroughfares.
+%
+Naturalistic field operational testing is a popular approach to validate and verify the safety of autonomous vehicles by leaving the autonomous cars to drive freely on actual roads~\cite{kalra2016driving}.
+However, this method is inefficient and dangerous~\cite{gambi2019generating}, since attractive execution conditions (e.g.,  traffic situations that lead to traffic accidents) are hard or impossible to recreate, limiting the replicability of testing results~\cite{hasenau2019virtual}.
+An alternative approach is virtual testing that uses computer simulations aggregating different control procedures under numerous virtual road conditions and traffic patterns to generate diverse test cases to challenge the self-driving software~\cite{hasenau2019virtual}.
+Virtual testing enables automated test execution and can expose problems in autonomous software, including perception, planning, and decision-making systems.
+However, it requires the availability of accurate road maps and geometrical models (e.g., 3D models with textures and material properties) to achieve reliable simulations and photo-realism.
+Artists and domain experts by themselves usually create those maps and models following a manual, laborious, and expensive process.
+%
+Consequently, cartography is an essential building block to conduct thorough virtual testing of autonomous vehicles~\cite{althoff2018automatic}.
+
+% \begin{figure}[H]
+%   \centering
+%     \includegraphics[width=0.5\textwidth]{images/lanelets_00}
+%   \caption{Map representation by lanelets~\cite{bender2014lanelets}.}
+%   \label{fig:lanelets}
+% \end{figure}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.3\textwidth]{images/cubetown_1}
+    \includegraphics[width=0.3\textwidth]{images/cubetown_2}
+    \includegraphics[width=0.3\textwidth]{images/cubetown_3}
+  \caption{Sample driving scenarios generated by \tool from one intersection in the Cube Town map, one of the simplest maps available for the 2021 IEEE Test AI Challenge.
+Driving scenarios start at the dot, before entering  intersections, and end at the cross, after passing  intersections.
+  Top: left turn; Middle: right turn; Bottom: straight through.}
+  \label{fig:samples-cubetown}
+\end{figure}
+
+A detailed road map consists of sets of roads composed of lanes, their interconnections (e.g., intersections, junctions), and regulations; hence, it allows creating a coherent, rich (virtual) environment around the ego-vehicle and diversified driving scenarios~\cite{althoff2018automatic,bender2014lanelets}.
+%
+Among the existing formats to model road maps, in this work, we rely on notion of lanelets~\cite{bender2014lanelets}, an innovative concept for road representation adopted by many (see Section~\ref{subsect:lanelets}).
+%
+We rely on lanelets to identify road configurations (e.g., intersections) to create relevant driving scenarios and to generate simulation-based test cases that challenge the autonomous vehicle's software automatically.
+In other words, we abstract existing maps into the lanelets format, generate  relevant and diversified (abstract) driving scenarios from this representation, and instantiate them into concrete scenarios running in existing driving simulators.
+
+%\section{Introduction}
+In this paper, we present \tool that implements our approach and summarize its application in the context of the 2021 IEEE Test AI Challenge.
+\tool, which is dubbed after our names ---Stephan, Alessio, and Vuong--- and means "safe" in Italian, works under the consideration that because manually generated road maps are costly, testers must use (and re-use) them wisely and extensively.
+Consequently, it leverages existing maps and generates as many tests as possible.
+%
+However, since generating virtual tests without any guidance is not cost-effective either because not all the generated tests are relevant or because many tests are similar to each other, \tool follows a systematic approach to generate only relevant test cases and maximize their diversity.
+%. Hence, they are unlikely to discover new insights into the ego-vehicle's behavior. Therefore,
+
+In short, \tool takes a map in OpenDrive (.xodr) format, generates abstract driving scenarios involving intersections (see Figure~\ref{fig:samples-cubetown}) and selects only those scenarios that result in diversified trajectories of the ego-vehicle to become concrete scenarios.
+After selecting the concrete driving scenarios, \tool generates test cases implement them and execute those test cases on Ubuntu 20.04.2 LTS running top-end industrial driving simulation and tools such as the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto}} in accordance to the rules of the 2021 IEEE Test AI Challenge.
+%
+We released \tool freely at the following link:
+\begin{center}
+\href{https://github.com/TrackerSB/IEEEAITestChallenge2021}{https://github.com/TrackerSB/IEEEAITestChallenge2021}
+\end{center}
+
+\section{LGSVL Simulator}
+\label{subsect:lgsvl}
+The LGSVL is a high fidelity simulator that providing full-stack simulation to challenge the autonomous driving software \cite{rong2020lgsvl}.
+The core simulation engine is based on the Unity game engine \cite{rong2020lgsvl}, one of the best solutions for high fidelity, developer-friendly, cost-effective simulation environments in the industry \cite{craighead2008using}.
+The simulator provides a reliable communication bridge that allows the exchange of ROS, ROS2, and Cyber RT messages between the simulator and other Autonomous Driving stacks \cite{rong2020lgsvl}.
+Thus, it can enable software engineers to quickly testing their self-driving software without driving actual vehicles in such common stacks as Autoware and Baidu Apollo \cite{rong2020lgsvl} as illustrated in the Figure~\ref{fig:apollosim}.
+Moreover, additional features such as easily customize sensors, build and manage new controllable objects, adjust the core simulator' modules, and generate diversified scenarios of particular environments, the simulator can empower various simulation applications for autonomous driving and more \cite{rong2020lgsvl}.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.5\textwidth]{images/apollo-sim}
+  \caption{
+    Apollo running with LGSVL Simulator, via LGSVL Simulator Website (\href{https://www.svlsimulator.com/docs/archive/2020.06/apollo-master-instructions}{https://www.svlsimulator.com/docs/archive/2020.06/apollo-master-instructions}).
+    }
+  \label{fig:apollosim}
+\end{figure}
+
+\section{Lanelets}
+\label{subsect:lanelets}
+Lanelets are a novel concept to represent the map in both topological and geometrical terms that roughly correspond to (segments of) road lanes~\cite{bender2014lanelets}.
+Lanelets comprise a set of atomic, interconnected, and \emph{drivable} road segments defined by a left and right bound.
+Bounds are implemented as polylines (i.e., list of points) and implicitly define the traffic direction, which helps determine the route from the given point to the predefined destination~\cite{PekIV20}.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.5\textwidth]{images/lanelets_01}
+  \caption{An example of lanelets \cite{althoff2018automatic}.}
+  \label{fig:lanelets}
+\end{figure}
+
+As illustrated in Figure~\ref{fig:lanelets}, connecting lanelets establishes semantic relations among them and gives rise to road segments and complex road networks that include merge/join and intersections.
+For example, \emph{adjacent} lanelets share a bound while \emph{preceding/following} lanelets share start point and endpoint in accordance to their traffic directions~\cite{althoff2018automatic}.
+Notably, lanelets can overlap and share the same start point and endpoint; consequently, they can form complex intersections~\cite{Althoff2017a} and can be used as an intermediate format to represent existing maps~\cite{althoff2018automatic}.
+%
+As we detail later, \tool relies on those features to translate existing maps into the lanelets format, identify intersections, and define (abstract) driving scenarios.
+
+\section{Automatically Generating Diversified Tests from Existing Maps}
+This section describes our approach and the generated test scenarios. The following sections, instead, summarize achieved results and found problems.
+
+\begin{figure*}[t]
+\minipage{0.32\textwidth}
+\includegraphics[width=\linewidth]{images/distance_cubetown_2}
+\endminipage\hfill
+\minipage{0.32\textwidth}
+\includegraphics[width=\linewidth]{images/distance_cubetown_1}
+\endminipage\hfill
+\minipage{0.32\textwidth}%
+  \includegraphics[width=\linewidth]{images/distance_ba_2}
+\endminipage
+\caption{Examples of trajectories at increasing levels of similarity.
+We generated the leftmost (dist=$0$) and central (dist=$0.14$) examples from the Cube Town map, while we generated the rightmost example (dist=$1.72$) from the Borregas Avenue map.}
+\label{fig:similarity}
+\end{figure*}
+
+\subsection{\tool in a Nutshell}
+\tool is entirely automatic and can generate test cases that stress the ego-vehicle in many different ways, possibly involving obstacles that partially or completely occlude the lane in which the ego-vehicle is driving.
+
+Given a map in OpenDrive\footnote{\href{https://www.asam.net/standards/detail/opendrive/}{https://www.asam.net/standards/detail/opendrive}}  format, \tool 
+\begin{inparaenum}[(1)]
+\item identifies the intersections in the map and 
+\item generates abstract driving scenarios that force the ego-vehicle to plan legal trajectories to cross those intersections.
+Next, \item it selects driving scenarios that correspond to quantifiably different trajectories and
+\item generates test cases implementing them. 
+Finally, \item it generates even more test cases by placing static obstacles, i.e., parked Non-Playable Characters (NPC) vehicles, in front of the ego-vehicle.
 \end{inparaenum}
 
-We demonstrated \tool in the context of the 2021 IEEE Test AI Challenge
-by testing state-of-art self-driving car software using an industrial driving simulator.
-In a matter of minutes, \tool identified many relevant tests from five maps of different sizes and complexity (up to $170$ junctions) and selected $20\%$ of those test cases for execution in the best case.
+The following sections detail each step of the proposed approach.
+
+\subsection{Identifying Intersections}
+We use the opendrive2lanelet library~\cite{althoff2018automatic} to translate the original maps from the OpenDrive to the lanelets format.
+As discussed in Section~\ref{subsect:lanelets}, the lanelets organizes its format by relations using follow and adjacent and provides geometrical information (e.g., the shape of each lanelet) and semantic information.
+
+Despite this, its structure does not explicitly capture intersections; hence \tool implements a heuristic to identify them: First, it uses the geometric information about lanelets to identify overlapping lanelets, which are named as a predecessor, an intersection and a successor.
+Since overlapping lanelets are likely to belong to the same intersection, \tool groups lanelets that (transitively) overlap together, as demonstrated in Figure~\ref{fig:intersection_a}
 %
-The evaluation results showed that tests cases generated by \tool resulted in quantifiably different trajectories of the test subject and exposed issues in the test subject and its integration with the simulation platform.
-\alessio{Update numbers with missing maps}
-\end{abstract}
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.5\textwidth]{images/intersection01}
+  \caption{An example of an intersection constructed by Salvo.}
+  \label{fig:intersection_a}
+\end{figure}
 
-% CubeTown
-%1. 10 paths
-%2. distance 1.9: 8 paths
-%3. 10 cells: 5 paths
-%4. 12 intersections
-%BorregasAve
-%1. 28 paths
-%2. distance 1.9: 20 paths
-%3. 10 cells: 16 paths
-%4. 29 intersections
-%Shalun
-%1. 140 paths
-%2. distance 1.9: 110 paths
-%3. 10 cells: 33 paths
-%4. 169 intersections
+The intersections identified this way may be incomplete because some of the lanelets that logically belong to large and complex intersections may not overlap with the other lanelets already assigned to those intersections.
+Therefore, \tool identifies the missing lanelets as those that are adjacent to the lanelets already assigned to an intersection and include them.
+As a result, having identified the lanelets that compose intersections, \tool proceeded by generating driving scenarios can force the ego-vehicle to cross them.
 
-\begin{IEEEkeywords}
-\alessio{todo}
-\end{IEEEkeywords}
+\subsection{Generating Relevant Scenarios}
+Legal trajectories across intersections such as the ones reported in Figure~\ref{fig:samples-cubetown} define relevant driving scenarios.
+Legal trajectories follow the traffic directions encoded into the lanelets.
+Additionally, we limit \tool to consider the simplest form of legal trajectory, i.e., those that do not require the ego-vehicle to change lanes to pass the intersections.
+Therefore, one typical generated driving scenario will start on a given lane \emph{before} entering an intersection, continue on the same lane across the intersection, and end on the (logically) same lane \emph{after} the intersection.
+%
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.5\textwidth]{images/lanelet01}
+  \caption{An example of parts of intersection constructed by Salvo. (1) Starting on a given lane, (2) Entering an intersection, (3) Continue on the same lane.}
+  \label{fig:intersection_sf}
+\end{figure}
 
-\section{Introduction}
-\alessio{todo}
+\tool generates driving scenarios by selecting the lanelets that belong to an intersection (Figure~\ref{fig:intersection_sf}) and then including those lanelets outside the intersection that \emph{precede} and \emph{follow} the selected ones.
+Notably, because intersections have various configurations (e.g., number of entering and exiting lanes), the generated driving scenarios indeed force the ego-vehicle to turn left, turn right, or go straight through the intersection.
 
-%\section*{Acknowledgment}
+The generated scenarios are composed of the smallest number (i.e., three) of lanelets.
+This feature arguably increases the understandability of the resulting test cases but does not necessarily guarantee fast test executions.
+The lanelets that precede and follow an intersection might be extensive; hence, it may require some time to be fully traversed.
+Therefore, to reduce execution time, \tool places the ego-vehicle at a fixed distance before entering the intersection and sets the target position to reach at a fixed distance after passing the intersection.
+Because those distances are configurable, testers can control the duration of test executions and make them more predictable.
+
+\subsection{Selecting Diversified Scenarios}
+Up to this point, \tool has not considered the diversity of scenarios.
+It simply generates as many scenarios as possible to explore the possibilities offered by the input road map.
+However, many trajectories may stress the ego-vehicle similarly, for example, by forcing it to drive straight through the same intersections from multiple directions.
+Therefore, \tool filters out test cases that are too similar to each other; hence, improving testing cost-efficiency.
+
+This paper studies two (greedy) approaches for filtering out similar test cases based on distance and feature maps.
+
+\subsubsection{Filtering Similar Scenarios by Similarity}
+The first approach to select diversified scenarios is based on computing the similarity of the ego-vehicle' trajectories imposed by the driving scenarios.
+The chosen metric is Levenshtein distance because it can provide a numerical representation of how different two trajectories are by measuring how many \emph{edits} are required to change one trajectory into the other.
+Since each trajectory is an array of points, so an \emph{edit} could be an insertion, a deletion, or a substitution of a point.
+In theory, Levenshtein distance is calculated by initializing an  $m\times n$ matrix where each cell contains the Levenshtein distance between the first $m^{th}$ points of one trajectory and the first $n^{th}$ points of other.
+The goal is to compute and fill out the entire matrix from the upper left to the lower right corner.
+Following this way, the number in the bottom-right corner will be Levenshtein distance between both trajectories.
 %
-%The preferred spelling of the word ``acknowledgment'' in America is without 
-%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-%acknowledgments in the unnumbered footnote on the first page.
+
+Specifically, \tool calculates the iterative Levenshtein distance between pairs of trajectories and discards driving scenarios whose trajectories are not distant enough from (i.e., they are too similar to) the trajectories of the driving scenarios already selected (see Figure~\ref{fig:similarity}).
+%
+Testers can control the similarity between the trajectories using a configurable threshold to create larger or smaller test suites.
+
+A similar approach to select diverse trajectories was followed by Zohdinasab and co-author in a pilot study to identify road features relevant for testing lane keeping systems~\cite{zohdinasab2021deephyperion}.
+As \tool, they took inspiration for the computation of the iterative Levenshtein distance from the work of Riccio and Tonella~\cite{DBLP:conf/sigsoft/RiccioT20}.
+
+\subsubsection{Filtering Driving Scenarios using Feature Maps}
+The second approach to select diversified scenarios is based on the feature maps defined by Zohdinasab et al.~\cite{zohdinasab2021deephyperion}. 
+%
+\tool generates numerous driving scenarios containing different types of trajectories and features such as minimum curvature and direction coverage capturing high-level characteristics of those trajectories, which can be used to build feature maps.
+Those maps place driving scenarios in a two-dimensional space according to the values taken by their features.
+%
+Intuitively, trajectories with similar features are placed in nearby cells, whereas trajectories with different features are placed in distance cells (see Figure~\ref{fig:feature-maps}).
+
+\begin{figure*}[t]
+\minipage{0.32\textwidth}
+\includegraphics[width=\linewidth]{images/feature_cubetown}
+\endminipage\hfill
+\minipage{0.32\textwidth}
+\includegraphics[width=\linewidth]{images/two_roads_same_cell.png}
+\endminipage\hfill
+\minipage{0.32\textwidth}%
+  \includegraphics[width=\linewidth]{images/roads_different_cell.png}
+\endminipage
+\caption{Left: Example of feature map distance coverage (dc) $\times$ min radius (mr) generated by \tool from the Cube Town map.
+Central: Trajectories sampled from the same cell in the feature map.
+Right: Trajectories sampled from distance cells in the feature map.}
+\label{fig:feature-maps}
+\end{figure*}
+
+Given a feature map, \tool considers similar those trajectories that are placed in the same cells.
+Consequently, it selects from each cell at most one trajectory (i.e., driving scenario) as representative, while discards all the others.
+
+Notably using the feature maps, testers can easily quantify the coverage achieved by \tool by counting the number of cells that contain at least one driving scenario.
+Likewise, developers can use the feature maps to assess the "richness" of the input road maps (see Figure~\ref{fig:feature-maps-results}).
+
+% \begin{figure}[H]
+%   \centering
+%     \includegraphics[width=0.5\textwidth]{images/feature_borregasave_maps}
+%     \caption{Borregas Ave trajectories based 10-by-10 cells map.}
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%     \includegraphics[width=0.5\textwidth]{images/two_roads_same_cell.png}
+%     \caption{Example of two roads that belong to the same cell.}
+% \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%     \includegraphics[width=0.5\textwidth]{images/roads_different_cell.png}
+%     \caption{Example of three roads taken from different (distant) cells.}
+% \end{figure}
+
+\subsection{Generating Test Cases}
+\tool generates a set of diversified driving scenarios as a combination of lanelets.
+So it needs to transform them into test cases that can be executed as simulations and result either in passing or failing.
+\tool does so by implementing introductory test oracles that check if the ego-vehicle reaches the target location after the intersection within a predefined timeout and by using simple geometric transformations to place the ego-vehicle in the starting position and rotate it according to the geometry of the initial lanelets.
+
+However, doing so is not enough since the simulations may include additional elements, such as traffic lights that affect the test result.
+For example, if the ego-vehicle needs to pass a controlled intersection and the traffic light is red, the ego-vehicle must stop in front of it, which may cause the timeout to trigger a false positive.
+Therefore, to avoid such false positives, \tool programs any traffic lights on the expected trajectories to turn green when the ego-vehicle approaches them.
+
+\subsection{Spicing Up the Test Cases}
+The tests generated by \tool are plain: they stress the ability of the ego-vehicle to plan trajectories that pass intersections and keep the lane but involve no other element besides the ego-vehicle and possibly traffic lights.
+Therefore, we illustrate how those test cases can be extended by placing static obstacles on the course of the ego-vehicle by letting  \tool place parked vehicles on the roads.
+
+Our approach to ``spice up'' the test cases starts from an existing driving scenario and generate tests by placing NPC vehicles predefined positions between the ego-vehicle's initial position (i.e., the starting point of the driving scenario) and the intersection.
+Placing NPC vehicles results is partially or entirely occlusions of the lane, forcing the ego-vehicle to swerve or change lane.
+Default occlusions are partial, and \tool causes them by placing an NPC vehicle on the left or right side of the lane.
+Additionally, if the geometry of the intersection allows it, \tool places an NPC in the middle of the lane in front of the ego-vehicle, forcing it to switch lanes before entering the intersection.
+
+In summary, on top of the test cases that \tool can generate from a given map, testers can quickly generate up to four times more test cases by simply adding NPC vehicles in front of the ego-vehicle.
+As we did before, we decided to place up to one NPC vehicle per test case to keep the test cases as simple and understandable as possible.
+
+\subsection{Prototype}
+\tool is implemented as a Python (version 3.9) command-line application and currently integrated with the SVL driving simulator.\footnote{\href{https://www.svlsimulator.com/}{https://www.svlsimulator.com/}}
+% Specifically, we use Python 3.9, the libraries listed in the requirements.txt file, and the maps in OpenDrive format available in the SVL simulator.
+%
+We tested \tool on Ubuntu 20.04.2 LTS running the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto/}} in accordance to the rules of the 2021 IEEE Test AI Challenge.
+
+\section{Achieved Results and Found Problems}
+To evaluate \tool, we applied it to test Apollo Baidu on the following five maps that were available on the SVL Web site at the time the 2021 IEEE Test AI Challenge took place:
+
+\begin{enumerate}
+ \item Cube Town
+ \item Borregas Avenue
+ \item Shalun
+ \item GoMentum
+ \item San Francisco
+\end{enumerate}
+
+We selected those five maps according to the following criteria: size, number of intersections, and compatibility with the opendrive2lanelets library (see column \emph{Intersections} in Table~\ref{tab:results} and figures~5--9).
+
+As reported in Table~\ref{tab:results}, using those five maps, \tool identified more than a hundred intersections and generated more than a thousand driving scenarios that do not involve NPV vehicles.
+From those scenarios, \tool selected up to 50\% test cases for the execution using features maps, whereas using distance, it selected considerably more cases.
+
+\begin{table}[t]
+    \centering
+      \caption{\tool's Evaluation Results}
+      \label{tab:results}
+      \begin{tabular}{lrrrr}
+        \toprule
+        \multicolumn{1}{c}{\textbf{Map Name}}&
+        \multicolumn{1}{c}{\textbf{Intersections}}&
+        \multicolumn{1}{c}{\textbf{Total Tests}}&
+        \multicolumn{2}{c}{\textbf{Selected Tests}} \\
+        & & & Similarity & Feature Map\\
+        \midrule
+        Cube Town & 2 & 12 & 8 & 5\\
+        Borregas Ave & 2 & 28 & 20 & 16\\
+        Shalun & 14 & 149 & 124 & 33\\
+        Gomentum & 25 & 126 & 110 & 25\\
+        San Francisco & 89 & 806 & 535 & 52\\
+        \bottomrule
+      \end{tabular}
+\end{table}
+
+\begin{figure*}[!tp]
+\minipage{0.31\textwidth}
+  \includegraphics[width=\linewidth]{images/map_cubetown}
+  \includegraphics[width=\linewidth]{images/feature_cubetown}
+  \caption{Cube Town map.}
+\endminipage\hfill
+\minipage{0.31\textwidth}
+  \includegraphics[width=\linewidth]{images/map_borregasave}
+  \includegraphics[width=\linewidth]{images/feature_borregasave}
+  \caption{Borregas Ave map.}
+\endminipage\hfill
+\minipage{0.31\textwidth}%
+  \includegraphics[width=\linewidth]{images/map_shalun}
+  \includegraphics[width=\linewidth]{images/feature_shalun}
+  \caption{Shalun map.}
+\endminipage
+
+\minipage{0.31\textwidth}%
+  \includegraphics[width=\linewidth]{images/map_gomentum}
+  \includegraphics[width=\linewidth]{images/feature_gomentum}
+  \caption{Gomentum map.}
+\endminipage\hfill
+\minipage{0.31\textwidth}%
+  \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
+  \includegraphics[width=\linewidth]{images/feature_sanfrancisco.png}
+  \caption{San Francisco map.}
+\endminipage
+\minipage{0.31\textwidth}%
+    \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
+\endminipage
+\label{fig:feature-maps-results}
+\end{figure*}
+
+The execution of the generated test cases resulted in failed test cases caused by the test subject not reaching the target location in time.
+Since we take extra care to remove all possible causes of false positives (e.g., traffic lights and random traffic), this result suggests that the test subject could not plan a suitable trajectory in some cases.
+
+\section{Future Work}
+
+In the hope of capturing the intended aim of the challenge, we brainstormed possible ideas to implement for future work.
+We tried to "think out-of-the-box" while remaining pragmatic.
+Below we summarize two of such ideas.
+
+\paragraph{Parking Lot Madness}
+Create scenarios that take place inside parking lots to test features like Tesla's "Smart Summon".
+The idea is to check if the ego-vehicle can safely drive from a parking spot to the parking lot's exit despite pedestrians and other vehicles.
+Our vision is to generate scenarios by placing the ego-vehicle in different parking spots and controlling the placement and movement of non-ego cars and pedestrians to create various situations.
+
+\paragraph{To Pass or Not to Pass?}
+Check the behaviour of the ego vehicle while handling controlled intersections.
+The idea is to take any map, find where controlled intersections and traffic lights are, and (automatically) generate scenarios where the car must pass the various controlled intersections.
+%
+Concrete tests can be generated by changing which controlled intersection to pass, the direction that ego-vehicle should follow (e.g., turn right, go straight), and directly acting upon the traffic lights (e.g., flashing lights, turn it off).
+%
+Alternatively, we can also place the ego car in the middle of those intersections and try to "trap it there" by controlling the traffic lights.
+This additional arrangement will let us check whether the vehicle can adequately free controlled intersections or get stuck in the middle of it.
 

### 2021-08-20 paper/main.tex
Added new references and updated the intro

@@
 \newcommand{\tool}{\textsc{SALVO}\xspace}
+\newcommand{\challenge}{2021 IEEE Autonomous Driving AI Test Challenge\xspace}
 \newboolean{showcomments}
@@
 % %
-% We demonstrated \tool in the 2021 IEEE Test AI Challenge
+% We demonstrated \tool in the \challenge
 % by testing state-of-the-art self-driving car software using an industrial driving simulator.
@@
 %(3) to generate those test cases.\\
-%We demonstrated \tool at the 2021 IEEE Test AI Challenge by running state-of-the-art self-driving car software in an industrial driving simulator against our generated test cases.
+%We demonstrated \tool at the \challenge by running state-of-the-art self-driving car software in an industrial driving simulator against our generated test cases.
 %In a matter of minutes, \tool analyzed five maps of different complexity (from 2 to more than 15 intersections), identified more than 1100 relevant driving scenarios and selected on average half of them for actual test executions.
@@
 To address those issues, we propose \tool a fully automated approach to identify quantifiably diverse and critical driving scenarios that can be instantiated on existing high-definition maps and implement them in an industrial driving simulator as executable test cases.
-The evaluation of \tool in the context of the 2021 IEEE Test AI Challenge showed that it could analyze maps of different complexity and identify many critical driving scenarios in minutes.
+The evaluation of \tool in the context of the \challenge showed that it could analyze maps of different complexity and identify many critical driving scenarios in minutes.
 Furthermore, the tests \tool generated stressed a state-of-art self-driving car software in quantifiably diverse ways and exposed issues with its implementation.
@@
 \section{Introduction and Motivation}
-Self-driving cars promise to reduce traffic accidents \cite{peden2016status}, increase fuel efficiency \cite{zamzuri2016current} and enhance comfort %and safety for elders and disabled people 
- \cite{harper2016estimating}.
-Testing self-driving car software is laborious and challenging since their development is still in an early stage and testing them lacks of standardized procedures and established approaches \cite{gambi2019generating}.\par
+Self-driving cars promise to reduce traffic accidents \cite{peden2016status}, increase fuel efficiency~\cite{zamzuri2016current} and enhance comfort~\cite{harper2016estimating}.
+Testing self-driving car software is laborious and challenging since self-driving car's development is still in an early stage, and there is a lack of standardized procedures and established approaches \cite{gambi2019generating}.
+Therefore, many researchers and organizations are currently investigating testing approaches to increase the quality of autonomous vehicles before they roam the thoroughfares.
+%
+Naturalistic field operational testing is a popular approach to validate and verify the safety of autonomous vehicles that leaves them free to drive on actual roads.
+However, as discussed by Kalra and Paddock~\cite{kalra2016driving}, this method is inefficient since relevant execution conditions (e.g., traffic situations that lead to traffic accidents) are hard to observe and ineffective as dangerous situations are impossible to recreate.
+Those, in turn, make limit the replicability of natural field operational tests' results ~\cite{hasenau2019virtual}.
+An alternative approach is virtual testing, also known as simulation-based testing, which uses computer simulations to generate diverse test cases to challenge the self-driving software involving traffic patterns and numerous virtual road conditions~\cite{hasenau2019virtual}.
+Virtual testing enables automated test execution and can expose problems in autonomous software, including perception, planning, and decision-making systems.
+However, it requires the availability of accurate geometrical models (e.g., 3D models with textures and material properties) to achieve photo-realism, i.e., to close the simulation-to-reality gap~\cite{9207173}, and detailed road maps.
+Consequently, cartography is an essential building block to conduct thorough virtual testing of autonomous vehicles~\cite{althoff2018automatic}.
+Artists and domain experts cooperate to create those models and maps following a manual, laborious, and expensive process.
 
-Nevertheless, many researchers and organisations put a lot of effort in exploring and devising testing approaches to increase the quality of autonomous vehicles before they roam the thoroughfares.
-%
-Naturalistic field operational testing is a popular approach to validate and verify the safety of autonomous vehicles by leaving the autonomous cars to drive freely on actual roads~\cite{kalra2016driving}.
-However, this method is inefficient and dangerous~\cite{gambi2019generating}, since attractive execution conditions (e.g.,  traffic situations that lead to traffic accidents) are hard or impossible to recreate, limiting the replicability of testing results~\cite{hasenau2019virtual}.
-An alternative approach is virtual testing that uses computer simulations aggregating different control procedures under numerous virtual road conditions and traffic patterns to generate diverse test cases to challenge the self-driving software~\cite{hasenau2019virtual}.
-Virtual testing enables automated test execution and can expose problems in autonomous software, including perception, planning, and decision-making systems.
-However, it requires the availability of accurate road maps and geometrical models (e.g., 3D models with textures and material properties) to achieve reliable simulations and photo-realism.
-Artists and domain experts by themselves usually create those maps and models following a manual, laborious, and expensive process.
-%
-Consequently, cartography is an essential building block to conduct thorough virtual testing of autonomous vehicles~\cite{althoff2018automatic}.
-
-% \begin{figure}[H]
-%   \centering
-%     \includegraphics[width=0.5\textwidth]{images/lanelets_00}
-%   \caption{Map representation by lanelets~\cite{bender2014lanelets}.}
-%   \label{fig:lanelets}
-% \end{figure}
-
-\begin{figure}[H]
+\begin{figure}[t]
   \centering
@@
     \includegraphics[width=0.3\textwidth]{images/cubetown_3}
-  \caption{Sample driving scenarios generated by \tool from one intersection in the Cube Town map, one of the simplest maps available for the 2021 IEEE Test AI Challenge.
-Driving scenarios start at the dot, before entering  intersections, and end at the cross, after passing  intersections.
+  \caption{Sample driving scenarios generated by \tool from an intersection in the Cube Town map available for the \challenge.
+Driving scenarios begin before entering an intersection~($\bullet$) and end after passing it~($\times$).
 Top: left turn; Middle: right turn; Bottom: straight through.}
@@
 
-A detailed road map consists of sets of roads composed of lanes, their interconnections (e.g., intersections, junctions), and regulations; hence, it allows creating a coherent, rich (virtual) environment around the ego-vehicle and diversified driving scenarios~\cite{althoff2018automatic,bender2014lanelets}.
+Detailed road maps consist of roads composed of lanes, their interconnections (e.g., intersections, junctions), and traffic regulations controlling them (e.g., speed limit, traffic direction); hence, they allow testers to create rich, coherent, and diversified driving scenarios~\cite{althoff2018automatic,bender2014lanelets}.
 %
-Among the existing formats to model road maps, in this work, we rely on notion of lanelets~\cite{bender2014lanelets}, an innovative concept for road representation adopted by many (see Section~\ref{subsect:lanelets}).
+Among the existing formats to model road maps, in this work, we rely on the notion of \emph{lanelets}~\cite{bender2014lanelets}, an innovative concept for road representation adopted by many (see Section~\ref{subsect:lanelets}).
 %
-We rely on lanelets to identify road configurations (e.g., intersections) to create relevant driving scenarios and to generate simulation-based test cases that challenge the autonomous vehicle's software automatically.
-In other words, we abstract existing maps into the lanelets format, generate  relevant and diversified (abstract) driving scenarios from this representation, and instantiate them into concrete scenarios running in existing driving simulators.
+Specifically, we rely on the semantics encoded in the lanelets representation of existing maps to identify intersections and create relevant driving scenarios around and across them.
+In other words, we abstract existing maps into the lanelets format to generate relevant and diversified \emph{abstract} driving scenarios.
+Next, we instantiate those abstract scenarios into concrete ones and generate simulation-based test cases that automatically challenge the autonomous vehicle's software in existing driving simulators.
 
-%\section{Introduction}
-In this paper, we present \tool that implements our approach and summarize its application in the context of the 2021 IEEE Test AI Challenge.
-\tool, which is dubbed after our names ---Stephan, Alessio, and Vuong--- and means "safe" in Italian, works under the consideration that because manually generated road maps are costly, testers must use (and re-use) them wisely and extensively.
-Consequently, it leverages existing maps and generates as many tests as possible.
+In this paper, we present \tool that implements our approach and summarize its evaluation in the context of the \challenge.
+\tool, which is dubbed after the author's first names ---Stephan, Alessio, and Vuong--- and means ``safe'' in Italian, works under the consideration that because manually generated road maps are costly and valuable, testers must use (and re-use) them wisely and extensively.
+Consequently, and in contrast to many existing test case generators (e.g., ~\cite{DBLP:conf/icse/GambiMF19,DBLP:conf/icse/HuynhGF19,DBLP:conf/sigsoft/RiccioT20,DBLP:conf/issta/ZohdinasabRGT21,DBLP:conf/sbst/PanichellaGZR21}) that procedurally generate virtual roads, it leverages existing maps to generate as many tests as possible.
 %
 However, since generating virtual tests without any guidance is not cost-effective either because not all the generated tests are relevant or because many tests are similar to each other, \tool follows a systematic approach to generate only relevant test cases and maximize their diversity.
-%. Hence, they are unlikely to discover new insights into the ego-vehicle's behavior. Therefore,
 
-In short, \tool takes a map in OpenDrive (.xodr) format, generates abstract driving scenarios involving intersections (see Figure~\ref{fig:samples-cubetown}) and selects only those scenarios that result in diversified trajectories of the ego-vehicle to become concrete scenarios.
-After selecting the concrete driving scenarios, \tool generates test cases implement them and execute those test cases on Ubuntu 20.04.2 LTS running top-end industrial driving simulation and tools such as the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto}} in accordance to the rules of the 2021 IEEE Test AI Challenge.
+The current implementation of \tool takes existing maps in OpenDrive format~\cite{dupuis2010opendrive}, generates abstract driving scenarios involving intersections, and selects among them those that result in quantifiably different ego-vehicle trajectories (see Figure~\ref{fig:samples-cubetown}).
+Finally, it instantiates the selected scenarios in the industrial driving simulation SVL~Simulator~\cite{rong2020lgsvl} as test cases and automatically executes them.
 %
@@
 
-\begin{figure}[H]
+\begin{figure}[tp]
   \centering
@@
 
-A similar approach to select diverse trajectories was followed by Zohdinasab and co-author in a pilot study to identify road features relevant for testing lane keeping systems~\cite{zohdinasab2021deephyperion}.
+A similar approach to select diverse trajectories was followed by Zohdinasab and co-author in a pilot study to identify road features relevant for testing lane keeping systems~\cite{DBLP:conf/issta/ZohdinasabRGT21}.
 As \tool, they took inspiration for the computation of the iterative Levenshtein distance from the work of Riccio and Tonella~\cite{DBLP:conf/sigsoft/RiccioT20}.
@@
 \subsubsection{Filtering Driving Scenarios using Feature Maps}
-The second approach to select diversified scenarios is based on the feature maps defined by Zohdinasab et al.~\cite{zohdinasab2021deephyperion}. 
+The second approach to select diversified scenarios is based on the feature maps defined by Zohdinasab et al.~\cite{DBLP:conf/issta/ZohdinasabRGT21}. 
 %
@@
 %
-We tested \tool on Ubuntu 20.04.2 LTS running the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto/}} in accordance to the rules of the 2021 IEEE Test AI Challenge.
+We tested \tool on Ubuntu 20.04.2 LTS running the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto/}} in accordance to the rules of the \challenge.
 
 \section{Achieved Results and Found Problems}
-To evaluate \tool, we applied it to test Apollo Baidu on the following five maps that were available on the SVL Web site at the time the 2021 IEEE Test AI Challenge took place:
+To evaluate \tool, we applied it to test Apollo Baidu on the following five maps that were available on the SVL Web site at the time the \challenge took place:
 

### 2021-08-20 paper/main.tex
Fix typos, fix figure size. Revised up to Section 4

@@
 Finally, it instantiates the selected scenarios in the industrial driving simulation SVL~Simulator~\cite{rong2020lgsvl} as test cases and automatically executes them.
-%
-We released \tool freely at the following link:
+
+To promote further research and enable reproducibility of our results, we release \tool as open-source software.
+\tool's source code and instructions to configure and run it are available at the following link:
 \begin{center}
@@
 
-\section{LGSVL Simulator}
-\label{subsect:lgsvl}
-The LGSVL is a high fidelity simulator that providing full-stack simulation to challenge the autonomous driving software \cite{rong2020lgsvl}.
-The core simulation engine is based on the Unity game engine \cite{rong2020lgsvl}, one of the best solutions for high fidelity, developer-friendly, cost-effective simulation environments in the industry \cite{craighead2008using}.
-The simulator provides a reliable communication bridge that allows the exchange of ROS, ROS2, and Cyber RT messages between the simulator and other Autonomous Driving stacks \cite{rong2020lgsvl}.
-Thus, it can enable software engineers to quickly testing their self-driving software without driving actual vehicles in such common stacks as Autoware and Baidu Apollo \cite{rong2020lgsvl} as illustrated in the Figure~\ref{fig:apollosim}.
-Moreover, additional features such as easily customize sensors, build and manage new controllable objects, adjust the core simulator' modules, and generate diversified scenarios of particular environments, the simulator can empower various simulation applications for autonomous driving and more \cite{rong2020lgsvl}.
-
 \begin{figure}[tp]
@@
     \includegraphics[width=0.5\textwidth]{images/apollo-sim}
-  \caption{
-    Apollo running with LGSVL Simulator, via LGSVL Simulator Website (\href{https://www.svlsimulator.com/docs/archive/2020.06/apollo-master-instructions}{https://www.svlsimulator.com/docs/archive/2020.06/apollo-master-instructions}).
-    }
+  \caption{Apollo Baidu (right, bottom) running with the SVL Simulator~\cite{svl-website}}
   \label{fig:apollosim}
@@
 
+\section{SVL Simulator}
+\label{subsect:lgsvl}
+The SVL Simulator~\cite{rong2020lgsvl} is the driving simulation selected for the \challenge.
+It is an industrial driving simulator that provides the full simulation stack to test autonomous driving software: On one side, it provides a core simulation engine based on Unity for high fidelity, developer-friendly, cost-effective rigid-body simulation~\cite{craighead2008using}; on the other side, it provides a communication bridge that allows connecting existing autonomous driving stacks such as Autoware~\cite{DBLP:journals/micro/KatoTINTH15} and Apollo Baidu~\cite{apollo}~(see~Figure~\ref{fig:apollosim}).
+Moreover, the SVL Simulator implements additional features such as easily customizing sensors and an API that enables building and managing controllable objects, adjusting the core simulator's modules, and the automated generation and execution of driving scenarios.
+
 \section{Lanelets}
 \label{subsect:lanelets}
-Lanelets are a novel concept to represent the map in both topological and geometrical terms that roughly correspond to (segments of) road lanes~\cite{bender2014lanelets}.
-Lanelets comprise a set of atomic, interconnected, and \emph{drivable} road segments defined by a left and right bound.
-Bounds are implemented as polylines (i.e., list of points) and implicitly define the traffic direction, which helps determine the route from the given point to the predefined destination~\cite{PekIV20}.
+Lanelets are a novel concept to represent road maps in both topological and geometrical terms.
+Lanelets models \emph{drivable} road segments and roughly correspond to (segments of) road lanes~\cite{bender2014lanelets}.
+They are defined by left and right bounds implemented as polylines (i.e., list of points), connected to define complex road maps, and overlapping to form intersections, joins, and merges.
+Since lanelets encode allowed traffic directions, they help determine the route from a predefined starting point to a given destination~\cite{PekIV20}.
 
-\begin{figure}[H]
+\begin{figure}[tp]
   \centering
@@
 
-As illustrated in Figure~\ref{fig:lanelets}, connecting lanelets establishes semantic relations among them and gives rise to road segments and complex road networks that include merge/join and intersections.
-For example, \emph{adjacent} lanelets share a bound while \emph{preceding/following} lanelets share start point and endpoint in accordance to their traffic directions~\cite{althoff2018automatic}.
-Notably, lanelets can overlap and share the same start point and endpoint; consequently, they can form complex intersections~\cite{Althoff2017a} and can be used as an intermediate format to represent existing maps~\cite{althoff2018automatic}.
+As illustrated in Figure~\ref{fig:lanelets}, lanelets can be connected to establish semantic relations that form longer road segments, intersections, merges and joins, and complex road networks.
+Therefore
+they can be used as an intermediate format to represent existing road maps~\cite{althoff2018automatic}.
+For example, \emph{adjacent} lanelets share one of the two bounds while \emph{preceding/following} lanelets share start or end points in accordance to their traffic direction~\cite{althoff2018automatic}.
+Notably, lanelets that overlap and share start or end points form intersections~\cite{Althoff2017a}.
 %
-As we detail later, \tool relies on those features to translate existing maps into the lanelets format, identify intersections, and define (abstract) driving scenarios.
+As we detail later, \tool relies on those features to automatically identify the intersections in existing road maps by analyzing their lanelets representation and define (abstract) driving scenarios across them.
 
 \section{Automatically Generating Diversified Tests from Existing Maps}
-This section describes our approach and the generated test scenarios. The following sections, instead, summarize achieved results and found problems.
+This section describes our approach to analyze existing maps and generate sets of diversified driving scenarios using two metrics to establish tests diversity.
+Instead, the following sections present \tool's evaluation in the context of the \challenge, discuss the achieved results and describe promising ideas for future work.
 

### 2021-08-20 paper/main.tex
Up to section 4.C. New images and additional references

@@
 \begin{figure*}[t]
-\minipage{0.32\textwidth}
+\minipage{0.33\textwidth}
 \includegraphics[width=\linewidth]{images/distance_cubetown_2}
 \endminipage\hfill
-\minipage{0.32\textwidth}
+\minipage{0.33\textwidth}
 \includegraphics[width=\linewidth]{images/distance_cubetown_1}
 \endminipage\hfill
-\minipage{0.32\textwidth}%
+\minipage{0.33\textwidth}%
   \includegraphics[width=\linewidth]{images/distance_ba_2}
 \endminipage
-\caption{Examples of trajectories at increasing levels of similarity.
-We generated the leftmost (dist=$0$) and central (dist=$0.14$) examples from the Cube Town map, while we generated the rightmost example (dist=$1.72$) from the Borregas Avenue map.}
+\caption{Examples of similar trajectories.
+In each plot, we compare pairs of trajectories generated by \tool and report their similarity computed using standard metrics such as the iterative Levenshtein distance (IT~Distance) and Cosine similarity.
+For example, the first two plots result from the Cube Town map and illustrate cases of very similar roads, while the rightmost plot, which results from the Borregas Avenue map, shows partially overlapping trajectories.}
 \label{fig:similarity}
@@
 \subsection{\tool in a Nutshell}
-\tool is entirely automatic and can generate test cases that stress the ego-vehicle in many different ways, possibly involving obstacles that partially or completely occlude the lane in which the ego-vehicle is driving.
+\tool is entirely automatic and can generate test cases that stress the ego-vehicle in many different ways, possibly involving static obstacles that partially or completely occlude the lane in which the ego-vehicle is driving.
 
-Given a map in OpenDrive\footnote{\href{https://www.asam.net/standards/detail/opendrive/}{https://www.asam.net/standards/detail/opendrive}}  format, \tool 
-\begin{inparaenum}[(1)]
-\item identifies the intersections in the map and 
-\item generates abstract driving scenarios that force the ego-vehicle to plan legal trajectories to cross those intersections.
-Next, \item it selects driving scenarios that correspond to quantifiably different trajectories and
-\item generates test cases implementing them. 
-Finally, \item it generates even more test cases by placing static obstacles, i.e., parked Non-Playable Characters (NPC) vehicles, in front of the ego-vehicle.
+Given a map in OpenDrive format \tool \begin{inparaenum}[(1)]
+\item identifies the intersections the map contains, 
+\item generates abstract driving scenarios that force the ego-vehicle to plan trajectories to cross those intersections safely, \item selects abstract driving scenarios that maximize the diversity of the allegedly planned trajectories, and \item generates executable test cases implementing the selected abstract driving scenarios.
 \end{inparaenum}
+
+\tool can also extend the set of generated test cases by reusing existing ones and placing static obstacles, i.e., Non-Playable Characters (NPC) vehicles, in the lane occupied by the ego-vehicle.
+By doing so \tool achieves two secondary goals: first, it further increases the diversity of the generated tests, as the obstacles force the ego-vehicle to plan new trajectories; second, it allows testing the ego-vehicle's object detection and collision avoidance in addition to route planning and lane-keeping.
 
@@
 \subsection{Identifying Intersections}
-We use the opendrive2lanelet library~\cite{althoff2018automatic} to translate the original maps from the OpenDrive to the lanelets format.
-As discussed in Section~\ref{subsect:lanelets}, the lanelets organizes its format by relations using follow and adjacent and provides geometrical information (e.g., the shape of each lanelet) and semantic information.
 
-Despite this, its structure does not explicitly capture intersections; hence \tool implements a heuristic to identify them: First, it uses the geometric information about lanelets to identify overlapping lanelets, which are named as a predecessor, an intersection and a successor.
-Since overlapping lanelets are likely to belong to the same intersection, \tool groups lanelets that (transitively) overlap together, as demonstrated in Figure~\ref{fig:intersection_a}
-%
-\begin{figure}[H]
+\begin{figure}
   \centering
-    \includegraphics[width=0.5\textwidth]{images/intersection01}
-  \caption{An example of an intersection constructed by Salvo.}
-  \label{fig:intersection_a}
+    \includegraphics[width=0.95\columnwidth]{images/overlapping}
+  \caption{An example of an intersection constructed by \tool by transitively identifying overlapping lanelets.}
+  \label{fig:overlapping}
 \end{figure}
 
-The intersections identified this way may be incomplete because some of the lanelets that logically belong to large and complex intersections may not overlap with the other lanelets already assigned to those intersections.
-Therefore, \tool identifies the missing lanelets as those that are adjacent to the lanelets already assigned to an intersection and include them.
-As a result, having identified the lanelets that compose intersections, \tool proceeded by generating driving scenarios can force the ego-vehicle to cross them.
+\tool uses the opendrive2lanelet library~\cite{althoff2018automatic} to translate the original maps from the OpenDrive format to the lanelets format.
+As discussed in Section~\ref{subsect:lanelets}, lanelets are connected by relations like `follow` and `adjacent` that define their semantics and provide geometrical information (e.g., their shape).
+However, since the lanelets format lacks a standardized way to capture intersections explicitly, i.e., via formalized relations between lanelets, \tool implements a heuristic to identify them: 
+First, it uses geometric information about lanelets to identify overlapping lanelets (\mbox{Figure~\ref{fig:overlapping}-A} and \mbox{Figure~\ref{fig:overlapping}-B}) as they are likely to belong to the same intersection.
+Second, since not all the lanelets in the same intersection directly overlap with each other, \tool groups together lanelets that \emph{transitively} overlap (\mbox{Figure~\ref{fig:overlapping}-C}).
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.95\columnwidth]{images/nonoverlapping}
+  \caption{An example of an intersection constructed by \tool by exploiting the relationships among lanelets.}
+  \label{fig:nonoverlapping}
+\end{figure}
+
+The intersections identified this way may be incomplete because, in some cases, lanelets that logically should belong together do not overlap with the other lanelets already assigned to those intersections.
+The bolded lanelets in Figure~\ref{fig:nonoverlapping} exemplify two instances of this situation.
+\tool identifies those missing lanelets by leveraging the relations defining the lanelet network.
+For example, for the case reported in \mbox{Figure~\ref{fig:nonoverlapping}-A} \tool includes in the intersection Lanelet~$1$ because it is adjacent to a lanelet already assigned to that intersection, i.e., Lanelet~$2$.
+For the case reported in \mbox{Figure~\ref{fig:nonoverlapping}-B}, instead, \tool includes Lanelet~$1$ because it precedes Lanelet~$2$ that is adjacent to Lanelet~$3$, the successors of a lanelet already assigned to that intersection, i.e., Lanelet~$4$.
+%
+Noticeably, the heuristic implemented by \tool to identify intersections exploiting the relations between lanelets and without user input is different from the one proposed by Klischat et al.~\cite{DBLP:conf/itsc/KlischatLHA20} that instead relies on hierarchical clustering and requires the user to specify a minimum size for the intersection.
+
+After identifying the intersections in the map, \tool can generate driving scenarios that force the ego-vehicle to cross them.
 

### 2021-08-20 paper/main.tex
WIP on section 4

@@
 \subsection{Generating Relevant Scenarios}
-Legal trajectories across intersections such as the ones reported in Figure~\ref{fig:samples-cubetown} define relevant driving scenarios.
-Legal trajectories follow the traffic directions encoded into the lanelets.
-Additionally, we limit \tool to consider the simplest form of legal trajectory, i.e., those that do not require the ego-vehicle to change lanes to pass the intersections.
-Therefore, one typical generated driving scenario will start on a given lane \emph{before} entering an intersection, continue on the same lane across the intersection, and end on the (logically) same lane \emph{after} the intersection.
+\tool generates abstract driving scenarios that follow legal trajectories across intersections such as those reported in Figure~\ref{fig:samples-cubetown}.
+We define those trajectories as legal because they follow the traffic directions encoded into the lanelets.
+Additionally, we limit \tool to consider only the simplest form of such trajectories, i.e., those that do not require the ego-vehicle to switch lanes.
+Therefore, a typical driving scenario generated by \tool starts on a lane \emph{before} an intersection, continues on the same lane across that intersection, and finally ends on the (logically) same lane \emph{after} that intersection.
 %
-\begin{figure}[H]
+\begin{figure}
  \centering
-    \includegraphics[width=0.5\textwidth]{images/lanelet01}
-  \caption{An example of parts of intersection constructed by Salvo. (1) Starting on a given lane, (2) Entering an intersection, (3) Continue on the same lane.}
+  \includegraphics[width=\columnwidth]{images/lanelet01}
+ \caption{An example of an abstract driving scenario generated by \tool in the Cube Town map.
+The scenario  starts on a lane~(1), continues inside the intersection by following the lane~(2), and ends on the same lane after passing the intersection (3).}
  \label{fig:intersection_sf}
@@
 
-\tool generates driving scenarios by selecting the lanelets that belong to an intersection (Figure~\ref{fig:intersection_sf}) and then including those lanelets outside the intersection that \emph{precede} and \emph{follow} the selected ones.
-Notably, because intersections have various configurations (e.g., number of entering and exiting lanes), the generated driving scenarios indeed force the ego-vehicle to turn left, turn right, or go straight through the intersection.
+\tool generates driving scenarios by selecting the lanelets that belong to an intersection (Figure~\ref{fig:intersection_sf}) and then including those lanelets outside the intersection that precede and follow the selected ones.
+Notably, because intersections have various configurations (e.g., number of entering and exiting lanes), the generated driving scenarios can stress different behaviors of ego-vehicle by forcing it to turn left, turn right, or go straight through the intersection.
 
@@
 This feature arguably increases the understandability of the resulting test cases but does not necessarily guarantee fast test executions.
-The lanelets that precede and follow an intersection might be extensive; hence, it may require some time to be fully traversed.
+For example, the lanelets preceding or following an intersection may be long, requiring some time to be fully traversed during test execution.
 Therefore, to reduce execution time, \tool places the ego-vehicle at a fixed distance before entering the intersection and sets the target position to reach at a fixed distance after passing the intersection.
-Because those distances are configurable, testers can control the duration of test executions and make them more predictable.
+Because those distances are configurable, testers can control the duration of test executions and enable the generation of tests involving obstacles (see~Section~\ref{sec:spicing-up}).
 
 \subsection{Selecting Diversified Scenarios}
-Up to this point, \tool has not considered the diversity of scenarios.
-It simply generates as many scenarios as possible to explore the possibilities offered by the input road map.
-However, many trajectories may stress the ego-vehicle similarly, for example, by forcing it to drive straight through the same intersections from multiple directions.
-Therefore, \tool filters out test cases that are too similar to each other; hence, improving testing cost-efficiency.
+Up to this point, \tool does not take the diversity of scenarios into account as it simply generates as many scenarios as possible to explore the possibilities offered by the input road map.
+However, many legal trajectories may stress the ego-vehicle similarly; for example, they may force it to drive straight through the same intersections from multiple directions.
+Therefore, \tool filters out test cases that are too similar to each other to improve testing cost-efficiency.
 
-This paper studies two (greedy) approaches for filtering out similar test cases based on distance and feature maps.
+We experimented with two (greedy) approaches for filtering out similar test cases based on distance metrics and feature maps.
 
@@
 \subsection{Spicing Up the Test Cases}
+\label{sec:spicing-up}
 The tests generated by \tool are plain: they stress the ability of the ego-vehicle to plan trajectories that pass intersections and keep the lane but involve no other element besides the ego-vehicle and possibly traffic lights.

### 2021-08-20 paper/main.tex
Finished pass on section 4

@@
 \newcommand{\challenge}{2021 IEEE Autonomous Driving AI Test Challenge\xspace}
+
 \newboolean{showcomments}
@@
 \begin{abstract}
-% Testing self-driving car software using photo-realistic and accurate physical simulators is becoming a widely adopted practice.
-Simulators enable the automated execution of many tests that possibly implement safety-critical driving scenarios that are too dangerous to put into practice.
-However, despite the speed-up achieved by using simulators, fundamental challenges are yet to be addressed before achieving cost-effective testing of self-driving cars.
-% %
-% In this paper, we present \tool, an approach to automated self-driving car software testing that addresses some of those challenges. Specifically, \tool
-% \begin{inparaenum}[(i)]
-% \item systematically identifies relevant driving scenarios among a myriad of potential driving scenarios that can be defined over existing maps;
-% \item selects driving scenarios that reduce testing efforts while ensuring quantifiable different behaviors, and 
-% \item automatically generates test cases that implement those diversified driving scenarios.
-% \end{inparaenum}
-% %
-% We demonstrated \tool in the \challenge
-% by testing state-of-the-art self-driving car software using an industrial driving simulator.
-% In a matter of minutes, \tool analyzed five maps of different complexity levels (from $2$ to more than $15$ intersections), identified more than $1100$ relevant driving scenarios, and selected on average half of them for the execution.
-% %
-% The evaluation results showed that tests cases generated by \tool from the selected driving scenarios resulted in quantifiable different trajectories followed by the test subject and exposed issues in it.
-
-%For testing self-driving cars simulations are heavily utilized since these allow running many simulations at once and allow enforcing critical situations without endangering any other drivers or pedestrians.
-%For increasing the quality of tests photo-realistic maps and accurate physical simulators are a widely adopted and still growing practice.
-%However, despite these advantages there are still fundamental challenges including cost-effectiveness and further increasing the degree of automation for finding or generating critical tests.\\
-%This paper presents \tool, an approach
-%(1) to systematically identify relevant driving scenarios among the myriad of potential driving scenarios,
-%(2) to select scenarios that reduce the required overall testing efforts by ensuring quantifiability and diversity of the expected behaviours of self-driving cars for succeeding scenarios and
-%(3) to generate those test cases.\\
-%We demonstrated \tool at the \challenge by running state-of-the-art self-driving car software in an industrial driving simulator against our generated test cases.
-%In a matter of minutes, \tool analyzed five maps of different complexity (from 2 to more than 15 intersections), identified more than 1100 relevant driving scenarios and selected on average half of them for actual test executions.
-%The evaluation results showed that the generated test cases resulted in quantifiable and diverse trajectories and exposed issues of the self-driving car software.
-
 Simulation-based tests are more cost-effective and less dangerous than field tests; hence, they are becoming the norm for thoroughly testing self-driving cars in virtual environments.
@@
 Therefore, \tool filters out test cases that are too similar to each other to improve testing cost-efficiency.
-
-We experimented with two (greedy) approaches for filtering out similar test cases based on distance metrics and feature maps.
+%
+We experimented with two (greedy) approaches for filtering out test cases based on distance metrics and feature maps.
 
 \subsubsection{Filtering Similar Scenarios by Similarity}
-The first approach to select diversified scenarios is based on computing the similarity of the ego-vehicle' trajectories imposed by the driving scenarios.
-The chosen metric is Levenshtein distance because it can provide a numerical representation of how different two trajectories are by measuring how many \emph{edits} are required to change one trajectory into the other.
-Since each trajectory is an array of points, so an \emph{edit} could be an insertion, a deletion, or a substitution of a point.
-In theory, Levenshtein distance is calculated by initializing an  $m\times n$ matrix where each cell contains the Levenshtein distance between the first $m^{th}$ points of one trajectory and the first $n^{th}$ points of other.
-The goal is to compute and fill out the entire matrix from the upper left to the lower right corner.
-Following this way, the number in the bottom-right corner will be Levenshtein distance between both trajectories.
-%
-
-Specifically, \tool calculates the iterative Levenshtein distance between pairs of trajectories and discards driving scenarios whose trajectories are not distant enough from (i.e., they are too similar to) the trajectories of the driving scenarios already selected (see Figure~\ref{fig:similarity}).
+The first approach to select diversified scenarios relies on the similarity between the trajectories imposed by the driving scenarios on ego-vehicle.
+After an initial exploration considering standard metrics such as edit distance and cosine similarity (see~Figure~\ref{fig:similarity}), we decided to adopt the Levenshtein distance to quantify the similarity of generated scenarios.
+The Levenshtein distance quantifies the similarity between trajectories by measuring how many \emph{edits} are required to transform one trajectory into the other; the smaller the number of edits is, the more similar the two trajectories are.
+Notably, \tool can use the Levenshtein distance because we represent trajectories as coordinates arrays, and edits correspond to insertions, deletions, and substitutions of arrays' entries.
+Specifically, \tool calculates the Levenshtein distance between pairs of trajectories using the code provided by DeepJanus~\cite{DBLP:conf/sigsoft/RiccioT20} and discards all the driving scenarios whose trajectories are too similar to the trajectories of driving scenarios already selected.
 %
 Testers can control the similarity between the trajectories using a configurable threshold to create larger or smaller test suites.
+For completeness, in our evaluation we filtered out trajectories with a distance value smaller than $1.9$.
 
-A similar approach to select diverse trajectories was followed by Zohdinasab and co-author in a pilot study to identify road features relevant for testing lane keeping systems~\cite{DBLP:conf/issta/ZohdinasabRGT21}.
-As \tool, they took inspiration for the computation of the iterative Levenshtein distance from the work of Riccio and Tonella~\cite{DBLP:conf/sigsoft/RiccioT20}.
+%A similar approach to select diverse trajectories was followed by Zohdinasab and co-author in a pilot study to identify road features relevant for testing lane keeping systems~\cite{DBLP:conf/issta/ZohdinasabRGT21}.
+%As \tool, they took inspiration for the computation of the iterative Levenshtein distance from the work of Riccio and Tonella~\cite{DBLP:conf/sigsoft/RiccioT20}.
 
 \subsubsection{Filtering Driving Scenarios using Feature Maps}
-The second approach to select diversified scenarios is based on the feature maps defined by Zohdinasab et al.~\cite{DBLP:conf/issta/ZohdinasabRGT21}. 
-%
-\tool generates numerous driving scenarios containing different types of trajectories and features such as minimum curvature and direction coverage capturing high-level characteristics of those trajectories, which can be used to build feature maps.
-Those maps place driving scenarios in a two-dimensional space according to the values taken by their features.
-%
-Intuitively, trajectories with similar features are placed in nearby cells, whereas trajectories with different features are placed in distance cells (see Figure~\ref{fig:feature-maps}).
+The second approach to select diversified scenarios utilizes the feature maps defined by Zohdinasab et al.~\cite{zohdinasab2021deephyperion}. 
+Trajectory features capture high-level characteristics of the abstract scenarios that are relevant for testing self-driving car software; examples of those features are the number of turns and the minimum curvature\footnote{The minimum curvature highlights the presence of sharp turns.} that quantify how difficult it would be to follow the trajectory.
+Instead, feature maps place driving scenarios in a two-dimensional space according to the values taken by their features and provide a compact and understandable representation of their most salient aspects.
+Intuitively, scenarios with similar features are placed in nearby cells, whereas scenarios that are far away in the map have very different features (see Figure~\ref{fig:feature-maps}).
 
 \begin{figure*}[t]
-\minipage{0.32\textwidth}
+\minipage{0.33\textwidth}
 \includegraphics[width=\linewidth]{images/feature_cubetown}
 \endminipage\hfill
-\minipage{0.32\textwidth}
+\minipage{0.33\textwidth}
 \includegraphics[width=\linewidth]{images/two_roads_same_cell.png}
 \endminipage\hfill
-\minipage{0.32\textwidth}%
+\minipage{0.33\textwidth}%
   \includegraphics[width=\linewidth]{images/roads_different_cell.png}
 \endminipage
-\caption{Left: Example of feature map distance coverage (dc) $\times$ min radius (mr) generated by \tool from the Cube Town map.
-Central: Trajectories sampled from the same cell in the feature map.
-Right: Trajectories sampled from distance cells in the feature map.}
+\caption{Examples of feature map and trajectories for the Cube Town map. 
+Left panel: The feature map generated by \tool using direction coverage (dc) and minimum radius (mr) as features.
+Central panel: Similar trajectories sampled from the same cell in the feature map, i.e., $(6,1)$.  
+Right panel: Diverse trajectories sampled from distant cells in the feature map, i.e., $(10,2), (1,10), (6,1)$.}
 \label{fig:feature-maps}
@@
 
-Given a feature map, \tool considers similar those trajectories that are placed in the same cells.
-Consequently, it selects from each cell at most one trajectory (i.e., driving scenario) as representative, while discards all the others.
+\tool's goal is to generate driving scenarios that result in trajectories with different characteristics; therefore, given a feature map filled with all the generated trajectories, \tool selects from each cell at most one trajectory (i.e., driving scenario) as a representative for the class of trajectories with the same feature combination while discarding the others.
 
-Notably using the feature maps, testers can easily quantify the coverage achieved by \tool by counting the number of cells that contain at least one driving scenario.
-Likewise, developers can use the feature maps to assess the "richness" of the input road maps (see Figure~\ref{fig:feature-maps-results}).
-
-% \begin{figure}[H]
-%   \centering
-%     \includegraphics[width=0.5\textwidth]{images/feature_borregasave_maps}
-%     \caption{Borregas Ave trajectories based 10-by-10 cells map.}
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%     \includegraphics[width=0.5\textwidth]{images/two_roads_same_cell.png}
-%     \caption{Example of two roads that belong to the same cell.}
-% \end{figure}
-
-% \begin{figure}[H]
-%   \centering
-%     \includegraphics[width=0.5\textwidth]{images/roads_different_cell.png}
-%     \caption{Example of three roads taken from different (distant) cells.}
-% \end{figure}
+Notably, using the feature maps, testers can easily quantify the coverage achieved by \tool by counting the number of cells that contain at least one driving scenario.
+Likewise, content generators can use the feature maps to assess the ``richness'' of the road maps.
+%
+For example, figures~\ref{fig:feature-maps-cubetown}~--~\ref{fig:feature-maps-sanfrancisco} show the road map (top plot) and the corresponding feature map (bottom plot) for the five maps we used in the \challenge (see Section~\ref{sec:evaluation}).
+From those figures, we can make the following observations:
+\begin{inparaenum}[(1)]
+\item road maps of increasing complexity, i.e., maps that contain more intersections, result in feature maps that are more covered, 
+and \item road maps with a repetitive structure result in feature maps with very dark cells, i.e., cells that contain many trajectories with very similar features.
+\end{inparaenum}
 
 \subsection{Generating Test Cases}
-\tool generates a set of diversified driving scenarios as a combination of lanelets.
-So it needs to transform them into test cases that can be executed as simulations and result either in passing or failing.
-\tool does so by implementing introductory test oracles that check if the ego-vehicle reaches the target location after the intersection within a predefined timeout and by using simple geometric transformations to place the ego-vehicle in the starting position and rotate it according to the geometry of the initial lanelets.
-
-However, doing so is not enough since the simulations may include additional elements, such as traffic lights that affect the test result.
-For example, if the ego-vehicle needs to pass a controlled intersection and the traffic light is red, the ego-vehicle must stop in front of it, which may cause the timeout to trigger a false positive.
-Therefore, to avoid such false positives, \tool programs any traffic lights on the expected trajectories to turn green when the ego-vehicle approaches them.
+\tool defines abstract driving scenarios as combinations of lanelets.
+So it needs to concretize them into executable test cases featuring test oracles that check if the ego-vehicle reaches the target location and if it does so within a predefined timeout.
+Also, \tool must configure the driving simulation to place the ego-vehicle in the starting position and rotate it according to the road direction.
+However, doing so may not be enough to ensure that the generated tests are reliable and reproducible because the simulations include additional components with randomized behaviors that can affect the test results.
+For example, if the ego-vehicle needs to pass an intersection controlled by a traffic light, its state affects the behavior of the ego-vehicle: if the traffic light is red, the ego-vehicle must stop before it, which may cause the timeout to trigger a false positive.
+However, executing multiple times the same test may produce different results, hence flakiness, as the traffic light's initial state is initialized at random unless configured explicitly by the test.
+Therefore, to avoid false positives and reduce test flakiness, \tool programs the traffic lights on the expected trajectories to turn green when the ego-vehicle approaches them.
 
@@
 \label{sec:spicing-up}
-The tests generated by \tool are plain: they stress the ability of the ego-vehicle to plan trajectories that pass intersections and keep the lane but involve no other element besides the ego-vehicle and possibly traffic lights.
-Therefore, we illustrate how those test cases can be extended by placing static obstacles on the course of the ego-vehicle by letting  \tool place parked vehicles on the roads.
+The tests generated by \tool are diverse but plain: they stress the ability of the ego-vehicle to plan various trajectories to pass the intersections while keeping the lane but involve no other elements besides the ego-vehicle and the traffic lights.
+To further increase the diversity of the generated tests and enable testing additional features of the ego-vehicle such as object detection and collision avoidance, we let \tool extend the basic tests by placing static obstacles, i.e., NPC vehicles, on the course of the ego-vehicle.
 
-Our approach to ``spice up'' the test cases starts from an existing driving scenario and generate tests by placing NPC vehicles predefined positions between the ego-vehicle's initial position (i.e., the starting point of the driving scenario) and the intersection.
-Placing NPC vehicles results is partially or entirely occlusions of the lane, forcing the ego-vehicle to swerve or change lane.
-Default occlusions are partial, and \tool causes them by placing an NPC vehicle on the left or right side of the lane.
-Additionally, if the geometry of the intersection allows it, \tool places an NPC in the middle of the lane in front of the ego-vehicle, forcing it to switch lanes before entering the intersection.
+Our approach to ``spice up'' tests consists in placing an NPC vehicle in predefined positions between the ego-vehicle's initial position (i.e., the starting point of the driving scenario) and the intersection to pass such that the NPC vehicle partially or entirely occludes the lane that the ego-vehicles is supposed to keep.
+Default occlusions are partial and cause the ego-vehicle to swerve before entering the intersection; \tool can place the NPC vehicle either on the left or right side of the lane, but not both.
+Additionally, but only if the geometry of the intersection allows it, \tool can place the NPC in the middle of the lane in front of the ego-vehicle, forcing it to switch lanes before entering the intersection.
 
-In summary, on top of the test cases that \tool can generate from a given map, testers can quickly generate up to four times more test cases by simply adding NPC vehicles in front of the ego-vehicle.
-As we did before, we decided to place up to one NPC vehicle per test case to keep the test cases as simple and understandable as possible.
+In summary, on top of the diversified test cases that \tool generates from a given map, testers can quickly generate up to four times more test cases by simply letting \tool add NPC vehicles in front of the ego-vehicle.
+Notably, we limit \tool to place a single NPC vehicle per test case to keep them as simple and understandable as possible.
 
 \subsection{Prototype}
-\tool is implemented as a Python (version 3.9) command-line application and currently integrated with the SVL driving simulator.\footnote{\href{https://www.svlsimulator.com/}{https://www.svlsimulator.com/}}
-% Specifically, we use Python 3.9, the libraries listed in the requirements.txt file, and the maps in OpenDrive format available in the SVL simulator.
-%
-We tested \tool on Ubuntu 20.04.2 LTS running the SVL Simulator version 2021.01 and Apollo Baidu version 6.0 \footnote{\href{https://apollo.auto/}{https://apollo.auto/}} in accordance to the rules of the \challenge.
+We implemented \tool in Python (v3.9) as a command-line application and integrated it with the SVL driving simulator (v2021.01) in accordance to the rules of the \challenge.
+For the evaluation, we ran \tool on a gaming laptop running Ubuntu~20.04.2~LTS, the SVL driving Simulator, and Apollo Baidu (v6.0).
 
-\section{Achieved Results and Found Problems}
+\section{Achieved Results and Problems Found}
+\label{sec:evaluation}
+
 To evaluate \tool, we applied it to test Apollo Baidu on the following five maps that were available on the SVL Web site at the time the \challenge took place:
@@
   \caption{Cube Town map.}
+  \label{fig:feature-maps-cubetown}
 \endminipage\hfill
@@
   \caption{Borregas Ave map.}
+    \label{fig:feature-maps-borregas}
 \endminipage\hfill
@@
   \caption{Shalun map.}
+    \label{fig:feature-maps-shalun}
 \endminipage 
+\end{figure*}
 
+\begin{figure*}[!tp]
+\hfill
 \minipage{0.31\textwidth}%
@@
   \caption{Gomentum map.}
+    \label{fig:feature-maps-gomentum}
 \endminipage\hfill
@@
   \caption{San Francisco map.}
+    \label{fig:feature-maps-sanfrancisco}
 \endminipage
-\minipage{0.31\textwidth}%
-    \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
-\endminipage
-\label{fig:feature-maps-results}
+\hfill
+%\minipage{0.31\textwidth}%
+%    \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
+%\endminipage
 \end{figure*}

### 2021-08-20 paper/main.tex
Finished pass for CR

@@
 
+\usepackage{flushend}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \newboolean{showcomments}
-\setboolean{showcomments}{true}         
+\setboolean{showcomments}{false}         
 %\setboolean{showcomments}{false} 
@@
 \subsubsection{Filtering Driving Scenarios using Feature Maps}
-The second approach to select diversified scenarios utilizes the feature maps defined by Zohdinasab et al.~\cite{zohdinasab2021deephyperion}. 
+The second approach to select diversified scenarios utilizes the feature maps defined by Zohdinasab et al.~\cite{DBLP:conf/issta/ZohdinasabRGT21}. 
 Trajectory features capture high-level characteristics of the abstract scenarios that are relevant for testing self-driving car software; examples of those features are the number of turns and the minimum curvature\footnote{The minimum curvature highlights the presence of sharp turns.} that quantify how difficult it would be to follow the trajectory.
@@
 
-\tool's goal is to generate driving scenarios that result in trajectories with different characteristics; therefore, given a feature map filled with all the generated trajectories, \tool selects from each cell at most one trajectory (i.e., driving scenario) as a representative for the class of trajectories with the same feature combination while discarding the others.
+\tool's goal is to generate driving scenarios that result in trajectories with different characteristics; therefore, given a feature map filled with all the generated trajectories, \tool selects from each cell at most one trajectory (i.e., driving scenario) as the representative for the class of trajectories with the same feature combination while discarding the others.
 
@@
 
-\section{Achieved Results and Problems Found}
+\section{Evaluation}
 \label{sec:evaluation}
 
-To evaluate \tool, we applied it to test Apollo Baidu on the following five maps that were available on the SVL Web site at the time the \challenge took place:
+\subsection{Experimental Settings}
+We evaluated \tool according to the main objectives defined in the \challenge, i.e., generation of diverse tests, automated test generation and execution, and generation of tests that can find problems in Apollo Baidu, and the (limited) resources we had at the time the \challenge took place.
 
-\begin{enumerate}
- \item Cube Town
- \item Borregas Avenue
- \item Shalun
- \item GoMentum
- \item San Francisco
-\end{enumerate}
+Since we deem the first two objectives more relevant than the last one, we devoted more effort to address them.
+Consequently, we evaluated the ability of \tool to generate diverse and executable test cases automatically using various maps available for the SVL Simulator, but run the tests against Apollo Baidu only for one map.
 
-We selected those five maps according to the following criteria: size, number of intersections, and compatibility with the opendrive2lanelets library (see column \emph{Intersections} in Table~\ref{tab:results} and figures~5--9).
+As summarized in Table~\ref{tab:results-generation}, we selected five maps of increasing size (see figures~\ref{fig:feature-maps-cubetown}~--~\ref{fig:feature-maps-sanfrancisco}) and complexity (see column \emph{Intersections} in Table~\ref{tab:results-generation}).
+Our selection was limited by the availability of the maps and their compatibility with the opendrive2lanelets library.
+%
+As summarized in Table~\ref{tab:results-effectiveness}, we tested Apollo Baidu only on the Cube Town map with all the test cases generated from the plain scenarios selected using similarity and feature maps (columns \emph{Plain}) and some test cases generated by placing NPC vehicles (columns \emph{NPC}).
+Specifically, we created the NPC tests by randomly sampling three selected scenarios from each set and placing the NPC vehicle on the ego-vehicle's left, right, and front.
+The table reports the number of failed test cases followed by the number of total tests executed.
 
-As reported in Table~\ref{tab:results}, using those five maps, \tool identified more than a hundred intersections and generated more than a thousand driving scenarios that do not involve NPV vehicles.
-From those scenarios, \tool selected up to 50\% test cases for the execution using features maps, whereas using distance, it selected considerably more cases.
+\subsection{Achieved Results}
 
@@
     \centering
-      \caption{\tool's Evaluation Results}
-      \label{tab:results}
+      \caption{\tool's Evaluation Results: Test Generation and Selection}
+      \label{tab:results-generation}
       \begin{tabular}{lrrrr}
@@
         \multicolumn{1}{c}{\textbf{Intersections}}&
-        \multicolumn{1}{c}{\textbf{Total Tests}}&
-        \multicolumn{2}{c}{\textbf{Selected Tests}} \\
-        & & & Similarity & Feature Map\\
+        \multicolumn{3}{c}{\textbf{Test Cases}}\\ \cmidrule(lr){3-5}
+        & & Total & Similarity & Feature Map\\
         \midrule
@@
         San Francisco & 89 & 806 & 535 & 52\\
+        \midrule 
+        \textbf{Total} & 132 & 1121 & 797 & 131\\
         \bottomrule
@@
 
+As reported in Table~\ref{tab:results-generation}, \tool identified more than a hundred intersections and generated more than a thousand driving scenarios that do not involve NPC vehicles.
+From those scenarios, it selected between 7\% (San Francisco) and 57\% (Borregas Ave) scenarios for the execution using features maps, whereas using similarity, it selected considerably more cases (up to 87\% for Gomentum).
+
+These results suggest that \tool could handle maps of considerable size and effectively identify intersections in them.
+Furthermore, regarding test generation, it was able to identify many driving scenarios and selected among them different driving scenarios.
+The results also suggest that feature maps may be more stringent in selecting test cases than similarity computed using edit distance.
+However, this observation should be taken with care, as the number of selected test cases using feature maps depends on their configurations, i.e., the selected features and their granularity.
+
+\begin{table}[t]
+    \centering
+      \caption{\tool's Evaluation Results: Test Effectiveness}
+      \label{tab:results-effectiveness}
+      \begin{tabular}{l rr rr}
+        \toprule
+        \multicolumn{1}{c}{\textbf{Map Name}} &
+        \multicolumn{2}{c}{\textbf{Similarity}} & % \cmidrule(lr){3-5}
+	\multicolumn{2}{c}{\textbf{Feature Map}}\\ \cmidrule(lr){2-3}\cmidrule(lr){4-5}
+        & Plain & NPC & Plain & NPC \\
+        \midrule
+        Cube Town  & 3/8 & 1/3 & 0/5 & 1/3\\
+        \bottomrule
+      \end{tabular}
+\end{table}
+
+As reported in Table~\ref{tab:results-effectiveness}, the execution of the generated test cases resulted in some failed test cases despite the simplicity of the map.
+Noticeably, all the failures are caused by the test subject not reaching the target location in time, meaning that the ego-vehicle did not crash into the NPC vehicles nor left the lane but could not plan or execute a suitable trajectory.
+
+Regarding plain tests, we can observe that selecting tests using similarity resulted in more failures than selecting tests using the feature map.
+Instead, regarding NPC tests, we can observe that one test failed consistently in both configurations.
+Upon manual inspection of the failed tests, we noticed that the NPC vehicle was always parked in the middle of the ego-vehicle's lane.
+This observation suggests either the ego-vehicle failed to plan a trajectory that required to switch the lane or that, although we took extra care to remove possible causes of false positives (e.g., traffic lights, the minimal distance of the NPC car from the intersection), we may have missed something.
+For example, we may have oversight the possibility that ego-vehicle cannot invade the opposite traffic direction to pass the obstacle, forcing it to wait behind the obstacle indefinitely.
+
 \begin{figure*}[!tp]
-\minipage{0.31\textwidth}
+\hfill
+\minipage{0.33\textwidth}
   \includegraphics[width=\linewidth]{images/map_cubetown}
@@
 \endminipage\hfill
-\minipage{0.31\textwidth}
+\minipage{0.33\textwidth}
   \includegraphics[width=\linewidth]{images/map_borregasave}
@@
 \endminipage\hfill
-\minipage{0.31\textwidth}%
+\minipage{0.33\textwidth}%
   \includegraphics[width=\linewidth]{images/map_shalun}
@@
 \endminipage 
+\hfill
 \end{figure*}
 
-\begin{figure*}[!tp]
-\hfill
-\minipage{0.31\textwidth}%
+\begin{figure*}[p]
+\minipage{0.33\textwidth}%
   \includegraphics[width=\linewidth]{images/map_gomentum}
@@
 \endminipage\hfill
-\minipage{0.31\textwidth}%
+\minipage{0.33\textwidth}%
   \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
@@
 \hfill
-%\minipage{0.31\textwidth}%
-%    \includegraphics[width=\linewidth]{images/map_sanfrancisco.png}
-%\endminipage
 \end{figure*}
-
-The execution of the generated test cases resulted in failed test cases caused by the test subject not reaching the target location in time.
-Since we take extra care to remove all possible causes of false positives (e.g., traffic lights and random traffic), this result suggests that the test subject could not plan a suitable trajectory in some cases.
 
@@
 In the hope of capturing the intended aim of the challenge, we brainstormed possible ideas to implement for future work.
-We tried to "think out-of-the-box" while remaining pragmatic.
+We tried to ``think out-of-the-box'' while remaining pragmatic.
 Below we summarize two of such ideas.
@@
 \paragraph{Parking Lot Madness}
-Create scenarios that take place inside parking lots to test features like Tesla's "Smart Summon".
-The idea is to check if the ego-vehicle can safely drive from a parking spot to the parking lot's exit despite pedestrians and other vehicles.
-Our vision is to generate scenarios by placing the ego-vehicle in different parking spots and controlling the placement and movement of non-ego cars and pedestrians to create various situations.
+Create scenarios that take place inside parking lots to test features like ``Smart Summon.'' The idea is to check if the ego-vehicle can safely drive from a parking spot to the parking lot's exit despite pedestrians and other vehicles.
+Our vision is to generate scenarios by placing the ego-vehicle in different parking spots and controlling the placement and movement of NPC cars and pedestrians to create various critical situations.
 
 \paragraph{To Pass or Not to Pass?}
-Check the behaviour of the ego vehicle while handling controlled intersections.
-The idea is to take any map, find where controlled intersections and traffic lights are, and (automatically) generate scenarios where the car must pass the various controlled intersections.
+Check the behavior of the ego-vehicle while handling controlled intersections. 
+The idea is to take any map, find where controlled intersections and traffic lights are, and (automatically) generate scenarios where the car must pass the various controlled intersections, possibly "trapping`` the ego-vehicle in the middle of them by directly acting upon the traffic lights (e.g., flashing lights, turn lights off).
 %
-Concrete tests can be generated by changing which controlled intersection to pass, the direction that ego-vehicle should follow (e.g., turn right, go straight), and directly acting upon the traffic lights (e.g., flashing lights, turn it off).
+%Concrete tests can be generated by changing which controlled intersection to pass, the direction that ego-vehicle should follow (e.g., turn right, go straight), and directly acting upon the traffic lights (e.g., flashing lights, turn lights off).
 %
-Alternatively, we can also place the ego car in the middle of those intersections and try to "trap it there" by controlling the traffic lights.
-This additional arrangement will let us check whether the vehicle can adequately free controlled intersections or get stuck in the middle of it.
+%Alternatively, we can also place the ego-vehicle in the middle of controlled intersections and try to ``trap it there'' by controlling the traffic lights.
+This additional arrangement will let us check whether the vehicle can adequately free the controlled intersections or get stuck in the middle of them.
 

### 2021-08-21 paper/main.tex
CR version. And copy of the CR paper

@@
     \includegraphics[width=0.5\textwidth]{images/apollo-sim}
-  \caption{Apollo Baidu (right, bottom) running with the SVL Simulator~\cite{svl-website}}
+  \caption{Apollo Baidu (right, bottom) running with the SVL Simulator~\cite{svl-website}.}
   \label{fig:apollosim}
@@
 Lanelets are a novel concept to represent road maps in both topological and geometrical terms.
-Lanelets models \emph{drivable} road segments and roughly correspond to (segments of) road lanes~\cite{bender2014lanelets}.
-They are defined by left and right bounds implemented as polylines (i.e., list of points), connected to define complex road maps, and overlapping to form intersections, joins, and merges.
+Lanelets model \emph{drivable} road segments and roughly correspond to (segments of) road lanes~\cite{bender2014lanelets}.
+They are defined by left and right bounds implemented as polylines (i.e., list of points), connected to define complex road maps, and overlap to form intersections, joins, and merges (see Figure~\ref{fig:lanelets}).
 Since lanelets encode allowed traffic directions, they help determine the route from a predefined starting point to a given destination~\cite{PekIV20}.
@@
 
-As illustrated in Figure~\ref{fig:lanelets}, lanelets can be connected to establish semantic relations that form longer road segments, intersections, merges and joins, and complex road networks.
-Therefore
+Lanelets can be connected to establish semantic relations that form longer road segments, intersections, merges and joins, and complex road networks. Therefore
 they can be used as an intermediate format to represent existing road maps~\cite{althoff2018automatic}.
